---
title: "Old Fracture CHI 2019"
output: html_notebook
---

## Set-up packages // libraries and prepare for data import: 
```{r}
## Uncomment install.packages and run outside of notebook environment: 
## install.packages(c("psych" ,"xtable", "tidyverse", "jsonlite", "likert", "ggplot2", "ploty", "mosaic", "modelr", "broom"))

library(psych)
library(likert)
library(jsonlite)
library(ggplot2)
library(mosaic)
library(plotly)
library(modelr)
library(broom)
source("http://pcwww.liv.ac.uk/~william/R/crosstab.r")
theme_set(theme_classic())
```

## Set-up directories, import and clean data: 
```{r}
rm(list=ls())
setwd("/Users/allieblaising/desktop/bang/R") 
getwd()
dataPath = "../.data"
## Define function to extract survey results: 
extractSurvey = function(frame,survey) {
  rounds = seq(1,length(frame$results.format[[1]]))
  roundResponses = lapply(rounds, function(round) {
    getCol = paste("results.",survey,".",round, sep="")
    surveyCols = Filter(function(x) grepl(getCol,x),names(frame))
    newCols = lapply(surveyCols, function(x) gsub(getCol,paste("results.",survey, sep=""),x) )
    surveyFrame = frame[,surveyCols]
    if (is.null(newCols)) {return("No newCols")}
    names(surveyFrame) = newCols
    surveyFrame$id = frame$id
    surveyFrame$round = round
    surveyFrame$batch = frame$batch
    surveyFrame$rooms = frame$rooms
    surveyFrame$manipulation = frame$results.manipulationCheck
    surveyFrame$blacklist = frame$results.blacklistCheck
    return(surveyFrame)
  })
  return(Reduce(rbind, roundResponses))
}
#Find directory for import (be sure to verify that batch #s align from bangData import and imports below): 
batches = dir(dataPath, pattern = "^[0-9]+$" )
completeBatches = Filter(function(batch) { 
  if (any(dir(paste(dataPath,batch,sep="/")) == "batch.json") && (any(dir(paste(dataPath,batch,sep="/")) == "users.json")) ) {
    batchData = read_json(paste(dataPath,batch,"batch.json",sep="/"), simplifyVector = TRUE)
    return(any(batchData$batchComplete == TRUE))
  } 
  return(FALSE)
}, batches)
userFiles = lapply(completeBatches, function(batch) {
  userFile = read_json(paste(dataPath,batch,"users.json",sep="/"), simplifyVector=TRUE)
  return(flatten(userFile, recursive = TRUE))
})

## Retroactively find rooms from chat data: 
overlappingFiles = Reduce(function(x,y) merge(x, y, all=TRUE), userFiles)
roundsWithRooms = apply(overlappingFiles,1,function(x) {
  roomsForIndividual = lapply(seq(1,4),function(y) {
    x$room = x$rooms[y]
    x$round = y
    return(x)
  })
  return(Reduce(rbind, roomsForIndividual))
})
library(tidyverse)

## To filter for all batches before launch of Q15 + 16 + round 4: 

overlappingFiles <- overlappingFiles %>% filter(batch<="1536132233074")

```

## More cleaning before visualizations: 
```{r}
## Apply extract survey function to extract the right columns and rows for viability survey: 
survey = 'viabilityCheck'
frame <- extractSurvey(overlappingFiles, survey) 
## Reduce to vertically combine rows in roundwithRooms list:  
finalRounds = as.data.frame(Reduce(rbind,roundsWithRooms))
## Subset incomplete cases from viability survey dataframe, use manipulation check b/c required for complete observation: 
data <- frame[frame$manipulation!="",]
## Rename room to rooms so that both are retained in future merge: 
data <- rename(data, rooms = "rooms")
## Subset incomplete cases for final rounds dataframe: 
data2 <- finalRounds[finalRounds$results.manipulationCheck!="", ]
## Select only variables of interest from final rounds: 
data2 = data2 %>% select(id, batch, room, bonus, name, friends, 
                         friends_history, results.condition, results.format,
                  results.manipulation,results.manipulationCheck,results.blacklistCheck, round)
## Convert to compatible data types before merge (**this should be simplified**)
data2$batch <- unlist(data2$batch)
data2$round <- unlist(data2$round)
data2$id <- unlist(data2$id) 
data$batch <- unlist(data$batch)

## Before merge, data and data2 should have the same # of observations
## Merge columns by id, round and batch #s: 
data <- left_join(data, data2, by=NULL)
## Subset only observations with batch #s in complete batches 
allConditions <- data[data$batch %in% completeBatches, ]
```
## Conditionally assign conditions based on treatment and results column: 
```{r}
## Messy, but robust? Verify, verify, verify people:   
data <- data %>% mutate(
  condition = case_when(
    results.condition=='treatment' & results.format=="c(1, 2, 1)" & round==1 ~ "A", 
    results.condition=='treatment' & results.format=="c(1, 2, 1)" & round==2 ~ "B", 
    results.condition=='treatment' & results.format=="c(1, 2, 1)" & round==3 ~ "Ap", 
    results.condition=='treatment' & results.format=="c(1, 1, 2)" & round==1 ~ "A", 
    results.condition=='treatment' & results.format=="c(1, 1, 2)" & round==2 ~ "Ap", 
    results.condition=='treatment' & results.format=="c(1, 1, 2)" & round==3 ~ "B", 
    results.condition=='treatment' & results.format=="c(2, 1, 1)" & round==1 ~ "B", 
    results.condition=='treatment' & results.format=="c(2, 1, 1)" & round==2 ~ "A", 
    results.condition=='treatment' & results.format=="c(2, 1, 1)" & round==3 ~ "Ap" ,
    results.condition=='control' & results.format=="c(1, 2, 1)" & round==1 ~ "A", 
    results.condition=='control' & results.format=="c(1, 2, 1)" & round==2 ~ "B", 
    results.condition=='control' & results.format=="c(1, 2, 1)" & round==3 ~ "Ap", 
    results.condition=='control' & results.format=="c(1, 1, 2)" & round==1 ~ "A", 
    results.condition=='control' & results.format=="c(1, 1, 2)" & round==2 ~ "Ap", 
    results.condition=='control' & results.format=="c(1, 1, 2)" & round==3 ~ "B", 
    results.condition=='control' & results.format=="c(2, 1, 1)" & round==1 ~ "B", 
    results.condition=='control' & results.format=="c(2, 1, 1)" & round==2 ~ "A", 
    results.condition=='control' & results.format=="c(2, 1, 1)" & round==3 ~ "Ap" , 
    results.condition=='baseline' & results.format=="1:3" & round==1 ~ "A" ,
    results.condition=='baseline' & results.format=="1:3" & round==2 ~ "B" ,
    results.condition=='baseline' & results.format=="1:3" & round==3 ~ "C" 
  )) 


```

## Set-up for factors for viability questions: 
```{r}
data <- rename(data, "repeatTeam" = results.viabilityCheck.15)
## Remove observations where viability survey wasn't on (remove this line if we want to keep observations with viability off): 
data <- na.omit(data)
## Factor for visualizations: 
levels <- c("Strongly Disagree", "Disagree", "Neutral","Agree", "Strongly Agree") 
clean <- data %>% 
  mutate_at(.vars = vars(contains("results.viabilityCheck")), funs(factor(., levels = levels))) 
## Create a new dataframe that converts factors to numeric for statistical analyses:
stats <- clean %>% mutate_if(is.factor, as.numeric)
for (i in 1:nrow(stats)) {
  stats$sum[i] <- sum(stats[i,1:14])                          
} 
stats$median <- median(stats$sum)
stats$mean <- mean(stats$sum)
## Revalue repeat team: keep plyr b/c some weird R stuff requires library to be called directly (recode values to )
stats$repeatTeam <- plyr::revalue(stats$repeatTeam, c("Yes"="0", "No"="1"))
stats$repeatTeam <- plyr::revalue(stats$repeatTeam, c("Keep this team"="0", "Do not keep this team"="1"))
## Convert to compatible classes for team grouping: 
stats$repeatTeam <- as.numeric(stats$repeatTeam)
stats$results.condition <- unlist(stats$results.condition)
stats$results.format <- as.character(stats$results.format)
stats$room <- unlist(stats$room)
## Dplyr to group teams and summarise variables for each group: group_by to find teams and summarise to compact individual results into group level results (i.e. one row of variable results per team)
groupedProportion <- stats %>%
  group_by(room, batch, round, condition, results.condition, results.format) %>%  ## to-do: add group ID in storage db. 
  summarise(n=n(), mean=mean(sum), median=median(sum),prop=sum(repeatTeam)/n, groupID=runif(1,0,2)) %>% 
## Filter out all teams with n=1 (i.e. a person in a one person team) 
  filter(n==2)

## Individual proportion: 
individualProportion <- stats %>% group_by(round, batch, room) %>% 
  mutate(sum=sum, mean=mean(sum), median=median(sum), n=n(),prop=sum(repeatTeam)/n) %>% 
  filter(n>1)

## Table showing how many teams we've run in each condition combination:  
## print(table(groupedProportion$condition, groupedProportion$results.condition)) 
```

## Probability of fracture across teams and condition combinations: 
```{r}
## Define and initialize cut-off point for fracture: 
groupedProportionFracture <- groupedProportion %>%
  group_by(results.condition, condition) %>% 
  mutate(fracture = case_when (prop<.50 ~ "0", 
                                prop>=.50~ "1")) 

## Baseline: (we probably won't need this since we are artificially making baseline conditions)
# groupedProportionFractureBaseline <- 
#   groupedProportionFracture %>% 
# filter(results.condition=="baseline") %>% 
#   filter(id %in% condition=="A" & condition=="C")
# baselineFracture1 <- groupedProportionFractureBaseline %>% filter(condition=="A")
# baselineFracture2 <- groupedProportionFractureBaseline %>% filter(condition=="C")

# TO-DO: check if this is right--seems off

groupedProportionFractureBaseline <- groupedProportionFracture %>% filter(results.format=="c(1, 1, 2)" | results.format=="c(2, 1, 1)") %>% filter(round=="1" | round=="3") 
# baselineFracture1 <- groupedProportionFractureBaseline %>% filter(round=="1")
# baselineFracture2 <- groupedProportionFractureBaseline %>% filter(round=="3")
# baselineFracture1$fracture15 <- baselineFracture1$fracture
# baselineFracture2$test2 <- baselineFracture2$fracture
# ## Below only combines if teams are in both round 1 & 3 together: 
# baselineFracture <- left_join(baselineFracture1, baselineFracture2, by=NULL, drop=TRUE)

## Treatment: 
groupedProportionFractureTreatment <- groupedProportionFracture %>% 
filter(results.condition=="treatment")
treatmentFracture1 <- groupedProportionFractureTreatment %>% filter(condition=="A")
treatmentFracture2 <- groupedProportionFractureTreatment %>% filter(condition=="Ap")
treatmentFracture <- cbind(treatmentFracture1, treatmentFracture2)

## Control:  
groupedProportionFractureControl <- groupedProportionFracture %>% 
  filter(results.condition=="control") 
controlFracture1 <- groupedProportionFractureControl %>% filter(condition=="A")
controlFracture2 <- groupedProportionFractureControl %>% filter(condition=="Ap")
controlFracture <- cbind(controlFracture1, controlFracture2)

## Manipulation check: 
## Use individual proportion data frame b/c we're interested in looking at individuals that were in teams >n=1
teamPatterns <- "Team 1 and Team 2|Team 1 and Team 3|Team 2 and Team 3"
individualProportion$manipulationAnswerKey <- str_extract(individualProportion$results.manipulationCheck,teamPatterns) 
individualProportion$manipulationAnswers <- individualProportion$results.manipulation
individualProportion$results.condition = unlist(individualProportion$results.condition)
## Omit NAs and results that can't be processed: 
cleanManipulation <- individualProportion[with(individualProportion, grepl(teamPatterns, manipulationAnswers) & grepl(teamPatterns, manipulationAnswerKey)),]
## Transform into compatiable form: 
cleanManipulation$manipulationAnswers = unlist(cleanManipulation$manipulationAnswers)
```

## Section #1: Does fracture have continuity with prior measures?

## 1A: Report the % of correct guesses on the manipulation check: 
```{r}
## Treatment manipulation: 
treatmentManipulation <- cleanManipulation %>% group_by(id, results.condition, manipulationAnswers, manipulationAnswerKey) %>% filter(results.condition=="treatment") %>% 
  summarise(n=n()) 
## If user manipulation answers == manipulation answer key then add 1 
treatmentManipulation$correctAnswers <- sum(ifelse(treatmentManipulation$manipulationAnswers==treatmentManipulation$manipulationAnswerKey,1,0))
## Calculate percent of correct manipulation answers for treatment: 
treatmentManipulation <- treatmentManipulation %>% mutate(percentCorrect = (correctAnswers/(nrow(treatmentManipulation))))
print(treatmentManipulation)

## Control manipulation: 
controlManipulation <- cleanManipulation %>% group_by(id, results.condition, manipulationAnswers, manipulationAnswerKey) %>% filter(results.condition=="control") %>% 
  summarise(n=n()) 
## If user manipulation answers == manipulation answer key then add 1 
controlManipulation$correctAnswers <- sum(ifelse(controlManipulation$manipulationAnswers==controlManipulation$manipulationAnswerKey,1,0))
## Calculate percent of correct manipulation answers for control: 
controlManipulation <- controlManipulation %>% mutate(percentCorrect = (correctAnswers/(nrow(controlManipulation))))
print(controlManipulation)
## Proportion test comparing treatment manipulation percent correct with chance: 
```

## 1B: Proportion test comparing treatment manipulation percent correct with chance: 
```{r}
## ⅓ ~ 33% = chance, ~43 = treatment (FILL-IN EACH TIME YOU RUN WITH NEW DATA!)

propManipulation <- prop.test(x = c(33, 43), n = c(100, 100))
print(propManipulation)
```

## 1C: Logistic regression predicting binary fracture outcome from viability scales: 
```{r}
## Split data into 60% training and 40% testing data sets to test how well the model performs 
set.seed(123)
groupedProportionFracture$fracture <- as.numeric(groupedProportionFracture$fracture) 
sample <- sample(c(TRUE, FALSE), nrow(groupedProportionFracture), replace = T, prob = c(0.6,0.4))
train <- groupedProportionFracture[sample, ]
test <- groupedProportionFracture[!sample, ]

## Simple logistic regression: we will fit a logistic regression model in order to predict 
## the probability of fracture based on a team's average viability sum: 

model1 <- glm(fracture ~ mean, family = "binomial", data = train)
summary(model1)

## To assess the linear regression deviance, look at deviance in summary output, if 
## deviance == sum of sqaures in linear regression, null deviance == difference between 
## a model with only the intercept ("no mean predictors") and the a saturated model 
## a model with a theoretically perfect fit. Model deviance (residual deviance) should be lower 
## small values == better fit. 

tidy(model1)
## Coefficient estimtes from log regression characterize relationship between the predictor and 
## response variable on a log-odds scale, so binary increase from no fracture - fracture can be interpreted as associated with a decrease in mean viability sum. 

## More coefficient output: measure the confidence intervals and accuracy of the coefficent: 
confint(model1)

## Making predictions: 
## What is the probability of fracture given the following team mean viability scores: for example purposes: 40 and 65: 

predict(model1, data.frame(mean = c(50, 65)), type = "response")

## From the output, we can see that the probability of fracture decreases by ~40% when mean viability sum increases from 40 to 65. 

## Model evaluation & diagnostics: 
## How well does the model fit the data? And how accurate are the predictions on an out-of-sample data set?

## Residul assessment: 

model1_data <- augment(model1) %>% 
  mutate(index = 1:n())

ggplot(model1_data, aes(index, .std.resid, color = mean)) + 
  geom_point(alpha = .5) +
  geom_ref_line(h = 3)

## Validation of predicted values: 
## How well does the model perform when predicting the target variable on out-of-sample observations? 

test.predicted.m1 <- predict(model1, newdata = test, type = "response")

## Classification performance for each model on the test data. Output gives us a list of true / false positives: 

list(
  model1 = table(test$mean, test.predicted.m1 > 0.5) %>% prop.table() %>% round(3)) 

table(test$mean, test.predicted.m1 > 0.5)
```
## 1D: Graph of fracture/no fracture vs. mean/stdev viability scale
```{r}
## Overall: 
g <- ggplot(groupedProportionFracture, aes(factor(fracture), mean)) 
g + geom_boxplot(varwidth=T, fill="plum") + 
  labs(subtitle="Team fracture value vs. mean viability score: fracture >=0.50 across all conditions (n=2)", 
       x="",
       y="Numeric sum of viability measures questions (range: 7-70)") 

## By condition + format: 
g <- ggplot(groupedProportionFracture, aes(factor(fracture), mean)) 
g + geom_boxplot(varwidth=T, fill="plum") + 
  labs(subtitle="Team fracture value vs. mean viability score: fracture >=0.50 (n=2)", 
       x="",
       y="Numeric sum of viability measures questions (range: 7-70)") + facet_grid(condition ~ results.condition) 

ggplot(data=groupedProportionFracture, aes(fracture, mean)) + 
   geom_point() +
  stat_smooth(method = "lm", col = "red") + labs(main="Scatterplot of fracture value vs. mean for team viability sums across all conditions (n=2)") +  facet_grid(condition ~ results.condition) 

ggplot(data=groupedProportionFracture, aes(fracture, mean)) + 
   geom_point() +
  stat_smooth(method = "lm", col = "red") + labs(main="Scatterplot of fracture value vs. mean for team viability sums (n=2)") +  facet_grid(condition ~ results.condition) 
```

## Section #2: How often does fracture occur?

## 2A: P(binary fracture) histogram of fracture proportion (by team)
```{r}
## First make sure you've made ABC condition
ggplot(data=groupedProportion, aes(groupedProportion$prop)) + 
  geom_histogram(breaks=seq(0, 1, by=0.20), 
                 col="red", 
                 fill="green", 
                 alpha=.2) + labs(title="Frequency of team fracture proportions by condition and pattern sequence", 
                                  x="team fracture proportion", y="Count") + facet_grid(results.condition ~ .) 

library(MASS)     

## Test if whether fracture smoking habit is independent of condition at .05 significance level: 

chi = table(groupedProportionFracture$fracture, groupedProportionFracture$results.condition)  
chi
print(chisq.test(chi)) 
```

## 2B: What's the overall % of fracturing the second time? (by condition)
```{r}
## Filtering second time only: 
groupedProportionFracture$fracture <- as.numeric(groupedProportionFracture$fracture)

## TO-DO: review below code, worried it's incorrect: 

groupedProportionFractureSecond <- groupedProportionFracture %>% group_by(results.condition) %>% 
      filter(condition=="Ap") %>% 
      mutate(overallPercent = sum(as.numeric(fracture))) %>% 
      summarise(n=n(), overallPercent=unique(overallPercent)/n) 
print(groupedProportionFractureSecond)

## For baseline theoretical distribution: (to-do: look over this, worried also that it's wrong)

groupedProportionFractureSecondBase <- groupedProportionFractureBaseline %>% 
      filter(round=="3") %>% 
      summarise(n=n(), overallPercent=sum(as.numeric(fracture))/n) 
print(mean(groupedProportionFractureSecondBase$overallPercent))

## Set-up separate groups for proportion tests to answer: does unmasked fracture more/less than masked 
## and more/less than new pairs? 

## Control: 

## Proportion tests for each (TO-DO, figure out argument stuff: this doesn't seem like the right test to run for the question we're asking?) also, fill-this in every time you get new data: 


## Is the proportion of fracture in the second round significantly different in the two conditions (i.e. treatment + baseline) 
treatmentvsBaselineChange <- c(48, 49)
propFractureChangeTreatmentvsBase <- prop.test(x = c(treatmentvsBaselineChange), n = c(100, 100))
print(propFractureChangeTreatmentvsBase) 

## Is the proportion of fracture in the second round significantly different in the two conditions (i.e. control + baseline) 
controlvsBaselineChange <- c(40, 49)
propFractureChangeControlvsBase <- prop.test(x = c(controlvsBaselineChange), n = c(100, 100))
print(propFractureChangeControlvsBase)
```
## Section 3: How consistent is fracture? 

## 3A: calculating the conditional probabilities of fracture for each condition: 
```{r}
conditionalProbTreatment <- groupedProportionFractureTreatment %>% filter(condition=="A" | condition=="Ap")
tally(~fracture | condition, data = conditionalProbTreatment, format = "proportion")

conditionalProbControl <- groupedProportionFractureControl %>% filter(condition=="A" | condition=="Ap")
tally(~fracture | condition, data = conditionalProbControl, format = "proportion")

conditionalProbBaseline <- groupedProportionFractureBaseline  %>% filter(condition=="A" | condition=="C")
tally(~fracture | condition, data = conditionalProbBaseline, format = "proportion")

## If fractured the first time, what's the % of fracturing the second time? look at 1 and Ap combination for % in second time: 

## Compare both treatment and control with baseline as theoretical distribution: 
```

## 3B: Now investigating the big result: switch %: what's the % of pairs flipping their decisions?

```{r}
## Convert format before merge: *this can be simplified*: 

treatmentFracture2$fracture <- as.numeric(treatmentFracture2$fracture) 
treatmentFracture1$fracture <- as.numeric(treatmentFracture1$fracture) 
treatmentFracture$absFracture <- abs(treatmentFracture2$fracture-treatmentFracture1$fracture)

controlFracture1$fracture <- as.numeric(controlFracture1$fracture)
controlFracture2$fracture <- as.numeric(controlFracture2$fracture)
controlFracture$absFracture <- abs(controlFracture2$fracture-controlFracture1$fracture)

baselineFracture$fracture1 <- as.numeric(baselineFracture$fracture1) 
baselineFracture$fracture2 <- as.numeric(baselineFracture$fracture2) 
baselineFracture$absFracture <- abs(baselineFracture$fracture1-baselineFracture$fracture2)

## Results here seem fishy? Triple check my code for abs/sum? 

treatmentFractureAbsSum <- sum(treatmentFracture$absFracture) 
print(treatmentFractureAbsSum)
controlFractureAbsSum <- sum(controlFracture$absFracture)
print(controlFractureAbsSum)
## baselineFractureAbsSum <- sum(baselineFracture$absFracture) 


## Don't we want a proportion test here before adding / trying chi-squared? 

treatmentAbsChange=c(15) 
controlAbsChange=c(1)

## Using baseline as theoretical probability distribution 
## Treatment: 
chisq.test(treatmentAbsChange,p=baselineAbsChange)

## Control:
chisq.test(controlAbsChange,p=baselineAbsChange)
```

## Visualizing change: 

```{r}
## Visualize differences: 

dat <- data.frame(changesPerCondition= factor(c("Sum of absolute fracture change in treatment >=.50","Sum of absolute fracture change in control >=.50"), levels=c("Sum of absolute fracture change in treatment >=.50","Sum of absolute fracture change in control >=.50")),
                  fractureValueSwitch = c(15, 1))

p <- ggplot(data=dat, aes(x=changesPerCondition, y=fractureValueSwitch)) +
  geom_bar(stat="identity")
p <- ggplotly(p)
p
```








