---
title: "Fracture CHI 2019 Results: n=2"
output: html_document
fig_width: 3.5
fig_caption: yes
---

## Set-up packages // libraries and prepare for data import:
```{r echo=FALSE, include=FALSE, results='hide'}
library(jsonlite)
library(ggplot2)
library(lme4)
library(lmerTest)
library(pROC)
library(stargazer)
library(dplyr)
```

## Set-up directories, import and clean data:
```{r, include=TRUE, echo=TRUE}
rm(list=ls())
setwd("/Users/kevinlin/Documents/BANG/bang/R")
getwd()
dataPath = "../.data"
MINIMUM_BATCH_NUMBER = 1544640127133
# last 2 days 1537366991708
# start of final day  1537514940000

TEAM_SIZE = 3
MIN_FRACTURE_PERCENT = 0.5

## Function to extract blacklist surveys:
extractBlacklistSurvey = function(frame,survey) {
  rounds = seq(1,3)
  roundResponses = lapply(rounds, function(round) {
    getCol = paste("results.",survey,".",round, sep="")
    surveyCols = Filter(function(x) grepl(getCol,x),names(frame))
    newCols = lapply(surveyCols, function(x) gsub(getCol,paste("results.",survey, sep=""),x) )
    surveyFrame = as.data.frame(frame[,surveyCols])
    if (is.null(newCols)) {return("No newCols")}
    names(surveyFrame) = newCols
    surveyFrame$id = frame$id
    surveyFrame$round = round
    surveyFrame$batch = frame$batch
    #surveyFrame$room = frame$room
    surveyFrame$rooms = frame$rooms
    surveyFrame$manipulationCheck <- frame$results.manipulationCheck
    #surveyFrame$blacklist = frame$results.blacklistCheck
    return(surveyFrame)
  })
  return(Reduce(rbind, roundResponses))
}

## Seperate viability function to deal with different column types
extractViabilitySurvey = function(frame,survey) {
  rounds = seq(1,3)
  roundResponses = lapply(rounds, function(round) {
    getCol = paste("results.",survey,".",round, sep="")
    surveyCols = Filter(function(x) grepl(getCol,x),names(frame))
    newCols = lapply(surveyCols, function(x) gsub(getCol,paste("results.",survey, sep=""),x) )
    surveyFrame = as.data.frame(frame[,surveyCols])
    if (is.null(newCols)) {return("No newCols")}
    names(surveyFrame) = newCols
    surveyFrame$id = frame$id
    surveyFrame$round = round
    surveyFrame$batch = frame$batch
    surveyFrame$rooms = frame$rooms
    #surveyFrame$room = frame$room
    surveyFrame$manipulationCheck.1 = frame$results.manipulationCheck.1
    #surveyFrame$blacklist = frame$results.blacklistCheck
    return(surveyFrame)
    print(surveyFrame)
  dim(surveyFrame)
  })
  return(Reduce(bind_rows, roundResponses))
}

# Filter batches and convert JSON to data frames
options(scipen=999)
batches = dir(dataPath, pattern = "^[0-9]+$" )
batches <- as.numeric(batches)
batches = batches[batches>MINIMUM_BATCH_NUMBER]
batches = Filter(function(batch) {
  if (any(dir(paste(dataPath,batch,sep="/")) == "batch.json") && (any(dir(paste(dataPath,batch,sep="/")) == "users.json")) ) {
      batchData = read_json(paste(dataPath,batch,"batch.json",sep="/"), simplifyVector = TRUE)
      return(any(batchData$batchComplete == TRUE))
    }
    return(FALSE)
}, batches)

users <- Reduce(function(x,y) merge(x, y, all=TRUE), lapply(batches, function(batch) {
  userFile = read_json(paste(dataPath,batch,"users.json",sep="/"), simplifyVector=TRUE)
  return(flatten(userFile, recursive = TRUE))
}))

#users <- users %>%
#  select(-results.engagementFeedback.undefined, -results.qSixteenCheck.undefined, -results.qFifteenCheck.undefined,   -contains("results.viabilityCheck.0"))
#users <- na.omit(users)

usersRounds = as.data.frame(Reduce(rbind, apply(users,1,function(x) {
  roomsForIndividual = lapply(seq(1,3),function(y) {
    x$room = x$rooms[y]
    x$round = y
    return(x)
  })
  return(Reduce(rbind, roomsForIndividual))
})))

usersRounds <- usersRounds %>% mutate(id = as.character(id), batch=as.numeric(batch), round=as.numeric(round), room=as.character(room))
usersRounds <- usersRounds %>% select(id, batch, round, room)

## Use extract survey function to reformat survey data:
manipulationCheck <- usersRounds %>%
  left_join(users, by=c("id", "batch")) %>%
  mutate(room=room.x) %>%
  mutate(manipulation=results.manipulation) %>%
  mutate(manipulationCheck=results.manipulationCheck.1) %>%
  mutate(teamOrder=results.format) %>%
  mutate(condition=results.condition) %>%
  select(id, batch, room, round, manipulation, manipulationCheck, teamOrder, condition)
qFifteen <- extractBlacklistSurvey(users, 'qFifteenCheck')
qSixteen <- extractBlacklistSurvey(users, 'qSixteenCheck')
#viabilitySurvey <- extractViabilitySurvey(users, 'viabilityCheck')
```

# Now merge everything
```{r}
usersRounds <- manipulationCheck %>%
  left_join(qFifteen, by=c("id", "batch", "round")) %>%
  left_join(qSixteen, by=c("id", "batch", "round")) %>%
  #left_join(viabilitySurvey, by=c("id", "batch", "round")) %>%
  mutate(rooms = rooms.x, manipulation = as.character(manipulation)) %>%
  select(-manipulationCheck.1, -manipulationCheck.x, -manipulationCheck.y, -rooms, -rooms.x, -rooms.y)
#rm(list=c("qFifteen","qSixteen","viabilitySurvey","manipulationCheck"))
rm(list=c("qFifteen","qSixteen","manipulationCheck"))

usersRounds <- usersRounds %>% 
  mutate(condition = case_when(
    condition=="treatment" ~ "masked",
    condition=="control" ~ "unmasked"
  ))

# Conditionally assign conditions based on treatment and results column:
## Messy, but robust? Verify, verify, verify people:   
## For runs with 4 rounds:
usersRounds <- usersRounds %>% mutate(
  team = case_when(
    teamOrder=="c(1, 1, 2, 3)" & round==1 ~ "A",
    teamOrder=="c(1, 1, 2, 3)" & round==2 ~ "Ap",
    teamOrder=="c(1, 1, 2, 3)" & round==3 ~ "B",
    teamOrder=="c(1, 1, 2, 3)" & round==4 ~ "B",
    teamOrder=="c(1, 2, 1, 3)" & round==1 ~ "A",
    teamOrder=="c(1, 2, 1, 3)" & round==2 ~ "B",
    teamOrder=="c(1, 2, 1, 3)" & round==3 ~ "Ap",
    teamOrder=="c(1, 2, 1, 3)" & round==4 ~ "B",
    teamOrder=="c(2, 1, 1, 3)" & round==1 ~ "B",
    teamOrder=="c(2, 1, 1, 3)" & round==2 ~ "A",
    teamOrder=="c(2, 1, 1, 3)" & round==3 ~ "Ap",
    teamOrder=="c(2, 1, 1, 3)" & round==4 ~ "B",
    teamOrder=="c(2, 3, 1, 1)" & round==1 ~ "B",
    teamOrder=="c(2, 3, 1, 1)" & round==2 ~ "B",
    teamOrder=="c(2, 3, 1, 1)" & round==3 ~ "A",
    teamOrder=="c(2, 3, 1, 1)" & round==4 ~ "Ap",
    teamOrder=="c(2, 1, 3, 1)" & round==1 ~ "B",
    teamOrder=="c(2, 1, 3, 1)" & round==2 ~ "A",
    teamOrder=="c(2, 1, 3, 1)" & round==3 ~ "B",
    teamOrder=="c(2, 1, 3, 1)" & round==4 ~ "Ap",
    teamOrder=="c(1, 2, 3, 1)" & round==1 ~ "A",
    teamOrder=="c(1, 2, 3, 1)" & round==2 ~ "B",
    teamOrder=="c(1, 2, 3, 1)" & round==3 ~ "B",
    teamOrder=="c(1, 2, 3, 1)" & round==4 ~ "Ap"
  ))

## Factor for visualizations:
levels <- c("Strongly Disagree", "Disagree", "Neutral","Agree", "Strongly Agree")
usersRounds <- usersRounds %>%
  mutate_at(.vars = vars(contains("viabilityCheck")), funs(factor(., levels = levels)))
usersRounds$viabilityScale <- usersRounds %>%
  select(contains("viabilityCheck")) %>%
  mutate_all(as.numeric) %>%
  rowSums()
usersRounds <- usersRounds %>%
  select(-contains("viabilityCheck"))
rm("levels")

## Rename Q15 + Q16:
usersRounds <- usersRounds %>%
  mutate(fracture = results.qFifteenCheck == "Do not keep this team",
         fractureMeta = results.qSixteenCheck == "Do not keep this team") %>%
  select(-results.qFifteenCheck, -results.qSixteenCheck)

teamStats <- usersRounds %>%
  arrange(id) %>%
  group_by(room, batch, round, condition, team) %>%
  summarise(n=n(), 
            teamMeanViability=mean(viabilityScale), 
            teamMedianViability=median(viabilityScale), 
            teamProportionFracture=sum(fracture/n()),
            teamMembers = paste(id, collapse=", "))

# Filter down to only partners (dyads)
teamStats <- teamStats %>%
  filter(n>=TEAM_SIZE)
usersRounds <- teamStats %>%
  select(room, batch, round, teamProportionFracture, condition) %>%
  left_join(usersRounds, by=c("room", "batch", "round", "condition"))

## Table showing how many teams we've run in each condition combination:  
print(table(teamStats$condition, teamStats$team))

teamViability = teamStats$teamMeanViability
viabilityMean = mean(teamViability)
viabilitySD = sd(teamViability)*sqrt((length(teamViability)-1)/(length(teamViability)))

teamStats$viabilityZ = (teamStats$teamMeanViability - viabilityMean) / viabilitySD

## Define and initialize cut-off point for fracture:
teamStats <- teamStats %>%
  group_by(room, batch, round, condition) %>%
  mutate(teamFracture = case_when (teamProportionFracture<MIN_FRACTURE_PERCENT ~ FALSE,
                                teamProportionFracture>=MIN_FRACTURE_PERCENT ~ TRUE))

# now add whether the team fractured to data
usersRounds <- usersRounds %>%
  select(-teamProportionFracture, -team) %>%
  left_join(teamStats, by=c("room", "batch", "round", "condition"))

# did they guess correctly?
usersRounds$partnerFractured <- ifelse(usersRounds$teamProportionFracture == 0, FALSE,
                                ifelse(usersRounds$teamProportionFracture == 1, TRUE,
                                       ifelse(usersRounds$fracture, FALSE, TRUE)))
usersRounds$metaGuessedCorrectly <- usersRounds$fractureMeta == usersRounds$partnerFractured

data = usersRounds

# For exporting data
# teamStats$fracture = as.numeric(teamStats$teamFracture)
# write.csv(teamStats, file = "teamStats.csv")
```

### Manipulation Check

# R manipulationcheck
```{r, echo=TRUE}
manipulationCheckAccuracy = data %>%
  ungroup() %>%
  distinct(id, batch, condition, manipulation, manipulationCheck) %>%
  mutate(manipulationCheckCorrect = manipulation == manipulationCheck)

manipulationCheckAccuracyByCondition <- manipulationCheckAccuracy %>%
  group_by(condition) %>%
  summarise(numCorrect = sum(manipulationCheckCorrect), n=n(), accuracy = numCorrect/n, se = sqrt(accuracy*(1-accuracy)/n))
print(manipulationCheckAccuracyByCondition)
numRounds = lengths(data$teamOrder)[1] # split up the list of teams in order to figure out how many rounds they had
numSameTeam = 2 # number of times they meet with the same team
chanceManipulation <- (1/choose(numRounds, numSameTeam))

p <- ggplot(data=filter(manipulationCheckAccuracyByCondition, condition=="masked"), aes(x=condition, y=accuracy)) +
  geom_bar(stat="identity", fill="#2853C2", alpha=.7)+
  geom_hline(yintercept=chanceManipulation, size=1, color="grey") +   
  geom_errorbar(aes(ymin=accuracy-se, ymax=accuracy+se), width = 0.1) +
  scale_x_discrete(labels=c("Masked teams")) +
  scale_y_continuous(labels = scales::percent_format(1)) + 
  theme_classic() + labs(subtitle="", 
       x="",
       y="Accuracy at identifying\n the repeat collaborators")

pdf('manipulationcheck.pdf', width=3.5, height=2.5)
dev.off();
p
```

## 1B: Proportion test comparing treatment manipulation percent correct with chance:
# R manipulationcheckprop
```{r}
## Proportion test with treatment and chance: 
maskedAccuracy <- filter(manipulationCheckAccuracyByCondition, condition=="masked")
manipulationCheckChanceComparison <- prop.test(maskedAccuracy[1,]$numCorrect, maskedAccuracy[1,]$n, chanceManipulation)
print(manipulationCheckChanceComparison)


```



### Consistency of fracture
```{r}
fractureFirst <- teamStats %>%
  filter(team=="A")
fractureSecond <- teamStats %>%
  filter(team=="Ap")
fractureConsistency <- fractureFirst %>%
  ungroup() %>%
  left_join(fractureSecond, by=c("teamMembers", "batch", "condition"), suffix=c(".first", ".second"))
fractureConsistency$consistent <- fractureConsistency$teamFracture.first == fractureConsistency$teamFracture.second
fractureConsistency$continuous <- fractureConsistency$viabilityZ.first - fractureConsistency$viabilityZ.second
fractureConsistency$continuousAbs <- abs(fractureConsistency$continuous)
rm("fractureFirst","fractureSecond")

conditionConsistency <- fractureConsistency %>%
  group_by(condition) %>%
  summarise(
    numConsistent = sum(consistent), 
    n=n(), 
    percentConsistent=numConsistent/n, 
    se=sqrt(percentConsistent*(1-percentConsistent))/n,
    numContinuousAbs = viabilityMean - sum(continuousAbs),
    percentContinuous = numContinuousAbs / viabilityMean,
    seContinuous=sqrt(percentContinuous*(1-percentContinuous))/n
    )
print(conditionConsistency)


maskedConsistency <- fractureConsistency %>% filter(condition=="masked")
unmaskedConsistency <- fractureConsistency %>% filter(condition=="unmasked")
t.test(maskedConsistency$viabilityZ.first,maskedConsistency$viabilityZ.second,paired = TRUE)
t.test(unmaskedConsistency$viabilityZ.first,unmaskedConsistency$viabilityZ.second,paired = TRUE)
t.test(fractureConsistency$continuousAbs~fractureConsistency$condition, var.equal = TRUE)
t.test(fractureConsistency$continuousAbs~fractureConsistency$condition)

sd(maskedConsistency$continuousAbs)
sd(unmaskedConsistency$continuousAbs)

p <- ggplot(data=filter(conditionConsistency), aes(x=condition, y=percentConsistent)) +
  geom_bar(stat="identity", fill="#2853C2", alpha=.7)+
  geom_errorbar(aes(ymin=percentConsistent-se, ymax=percentConsistent+se), width = 0.1) +
  scale_x_discrete(labels=c("Masked teams","Unmasked teams")) +
  scale_y_continuous(labels = scales::percent_format(1)) + 
  theme_classic() + labs(subtitle="", 
       x="",
       y="Consistancy of fracture")

pdf('manipulationcheck.pdf', width=3.5, height=2.5)
dev.off();
p

p2 <- ggplot(data=filter(conditionConsistency), aes(x=condition, y=percentContinuous)) +
  geom_bar(stat="identity", fill="#2853C2", alpha=.7)+
  geom_errorbar(aes(ymin=percentContinuous-seContinuous, ymax=percentContinuous+seContinuous), width = 0.1) +
  scale_x_discrete(labels=c("Masked teams","Unmasked teams")) +
  scale_y_continuous(labels = scales::percent_format(1)) + 
  theme_classic() + labs(subtitle="", 
       x="",
       y="Consistancy of fracture")

pdf('manipulationcheck.pdf', width=3.5, height=2.5)
dev.off();
p2

# chisq.test(conditionConsistency$)

```

```{r}
library(lme4)
fractureConsistency$team = paste(fractureConsistency$batch,fractureConsistency$room.first,fractureConsistency$round.first,sep = )
summary(lmer(continuousAbs ~ condition + (1 | team), data=fractureConsistency))
```

## Section #1: Does fracture have continuity with prior measures?
## 1C: Logistic regression predicting binary fracture outcome from viability scales: 
# R viabilitydescriptive
```{r}
viabilityDescriptive <- describe(groupedProportionFracture$mean)
viabilityDescriptive

```

# R viabilitycheck
```{r}
groupedProportionFracture$logicalfracture <- groupedProportionFracture$fracture == "1"
describe(subset(groupedProportionFracture, logicalfracture == TRUE)$mean)
describe(subset(groupedProportionFracture, logicalfracture == FALSE)$mean)
t.test(groupedProportionFracture$mean ~ groupedProportionFracture$logicalfracture)

## Simple logistic regression: we will fit a logistic regression model in order to predict
## the probability of fracture based on a team's average viability sum:
groupedProportionFracture$fracture <- as.numeric(groupedProportionFracture$fracture)
groupedProportionFracture$logicalfracture <- as.logical(groupedProportionFracture$fracture)
model1 <- glm(logicalfracture ~ mean, family = "binomial", data = groupedProportionFracture)
stargazer(model1,
          covariate.labels = c("Average viability scale", "(Intercept)"),
          dep.var.labels=c("Fracture"),
          no.space=TRUE,
          title="The relationship between the viability scale and fracture. Higher viability was significantly associated with lower log odds of fracture.",
          label="tab:viability",
          #keep.stat="n",
          table.placement = "tb",
          star.cutoffs = c(0.05, 0.01, 0.001)
          )

summary(model1)

exp(cbind(coef(model1), confint(model1)))
```

## Test predictive power of logistic regression:
```{r, include=FALSE, }
## From output we see that a one unit decrease in mean viability score is associated with a decreasein the log odds of fracture by 0.26 units.

## Check predictive power:

## Split data into 60% training and 40% testing data sets to test how well the model performs
set.seed(123)
groupedProportionFracture$fracture <- as.numeric(groupedProportionFracture$fracture)
sample <- sample(c(TRUE, FALSE), nrow(groupedProportionFracture), replace = T, prob = c(0.6,0.4))
train <- groupedProportionFracture[sample, ]
test <- groupedProportionFracture[!sample, ]

model2 <- glm(fracture ~ mean, family = "binomial", data = train)
stargazer(model2, title="Training Results", align=TRUE)
summary(model2)
print(model2)
## To assess the linear regression deviance, look at deviance in summary output, if
## deviance == sum of sqaures in linear regression, null deviance == difference between. a model with only the intercept ("no mean predictors") and the a saturated model a model with a theoretically perfect fit. Model deviance (residual deviance) should be lower (i.e. small values == better fit).

print(tidy(model1))
print(tidy(model2))
## Coefficient estimtes from log regression characterize relationship between the predictor and
## response variable on a log-odds scale, so binary increase from no fracture - fracture can be interpreted as associated with a decrease in mean viability sum.

## More coefficient output: measure the confidence intervals and accuracy of the coefficent:
confint(model1)

## Making predictions:
## What is the probability of fracture given the following team mean viability scores: for example purposes: 55 and 65:

predict(model2, data.frame(mean = c(55, 65)), type = "response")

## From the output, we can see that the probability of fracture decreases from 0.31% to 0.03% when mean viability sum increases from 55 to 65.

## Another example, with means 45 and 60:

predict(model2, data.frame(mean = c(40, 60)), type = "response")

## From the output, we can see that the probability of fracture decreases from 0.96% to 0.10% when mean viability sum increases from 40 to 60.

## Model evaluation & diagnostics:
## How well does the model fit the data? And how accurate are the predictions on an out-of-sample data set?

## Residul assessment:
model1_data <- augment(model1) %>%
  mutate(index = 1:n())

ggplot(model1_data, aes(index, .std.resid, color = mean)) +
  geom_point(alpha = .5) +
  geom_ref_line(h = 3)

## Validation of predicted values:
## How well does the model perform when predicting the target variable on out-of-sample observations?

test.predicted.m1 <- predict(model1, newdata = test, type = "response")

## Classification performance for each model on the test data. Output gives us a list of true / false positives:

list(
  model1 = table(test$mean, test.predicted.m1 > 0.5) %>% prop.table() %>% round(3))

table(test$mean, test.predicted.m1 > 0.5)
```

```{r, include=FALSE, eval=FALSE}
## Logistic regression on individual score:
individualProportionFractureTreatment <- individualProportionFracture %>%
filter(results.condition=="treatment")
individualTreatmentFracture1 <- individualProportionFractureTreatment %>% filter(condition=="A")
individualTreatmentFracture2 <- individualProportionFractureTreatment %>% filter(condition=="Ap")
individualTreatmentFracture <- cbind(individualTreatmentFracture1, individualTreatmentFracture2)
## Need to finish this
```

## 1D: Graph of fracture/no fracture vs. mean/stdev viability scale

## Boxplot: mean viability survey scores + fracture value (group level + individual level)
# R viabilityplot
```{r, include=TRUE, echo=TRUE}
g <- ggplot(groupedProportionFracture, aes(factor(fracture), mean)) +
  geom_boxplot(varwidth=T, fill="#2853C2", alpha=0.7) +
  labs(
       x="",
       y="Average viability score") +
  scale_x_discrete(labels=c("0" = "No fracture", "1" = "Fracture")) + theme_classic()
  #theme(text = element_text(size=25), axis.text.x = element_text(size=16))
pdf('viabilityplot.pdf', width=3.5, height=2)
g
dev.off();

g <- ggplot(individualProportionFracture, aes(factor(fracture), sum))
g + geom_boxplot(varwidth=T, fill="#2853C2", alpha=0.7) +
  labs(x="",
       y="Individual viability score") +
 scale_x_discrete(labels=c("0" = "Keep this team", "1" = "Do not keep this team")) + theme_classic() + theme(text = element_text(size=25),
        axis.text.x = element_text(size=16))

```

```{r, include=FALSE, eval=FALSE}
## Correlation scatterplot: mean viability survey scores + fracture value (group level + individual level)
## Grouped fracture correlation:
ggplot(data=groupedProportionFracture, aes(fracture, mean)) +
   geom_point() +
  stat_smooth(method = "lm", col = "red") + labs(title="Scatterplot correlation between teams' mean viability and binary fracture scores", y="Teams' mean viability survey score (range 14-70) ", x="Teams' binary fracture score") +
scale_x_discrete(labels=c("0" = "Keep this team", "1" = "Do not keep this team"))

## Individual fracture correlation:
ggplot(data=individualProportionFracture, aes(fracture, mean)) +
   geom_point() +
  stat_smooth(method = "lm", col = "red") + labs(subtitle="Scatterplot correlation between individuals' mean viability and binary fracture scores", y="Individual mean viability survey scores (range 14-70) ", x="Individual binary fracture score") +
scale_x_discrete(labels=c("0" = "Keep this team", "1" = "Do not keep this team"))

## Grouped fracture proportion correlation:
ggplot(data=individualProportionFracture, aes(prop, mean)) +
   geom_point() +
  stat_smooth(method = "lm", col = "red") + labs(subtitle="Scatterplot correlation between teams' mean viability and team fracture proportion", y="Individual mean viability survey scores (range 14-70 ", x="Teams' fracture proportion") +
scale_x_continuous(labels=c("0" = "Keep this team", "0.40", "0.60", "0.80" ,"1.00" = "Do not keep this team"))
```

## Group by and summarise fracture percentage by condition + plot for percentages:
```{r, echo=TRUE}
resultsPercent <- groupedProportionFracture %>% group_by(results.condition) %>% summarise(n=n(), fracture=sum(fracture), percent=fracture/n, se=sqrt(percent*(1-percent)/n)) %>% filter(results.condition=="control" | results.condition=="treatment")
dat <- data.frame(conditionFracturePercent= factor(c("Unmasked","Masked"), levels=c("Unmasked","Masked")),
                  fractureTotal = c(resultsPercent$percent), se=c(resultsPercent$se))  
dat$fractureTotal <- round(dat$fractureTotal, 3)

p <- ggplot(data=dat, aes(x=conditionFracturePercent, y=fractureTotal)) +
  geom_bar(stat="identity", fill="#2853C2", alpha=0.7)+
  scale_y_continuous(labels = scales::percent_format(10)) +
  geom_text(aes(label=fractureTotal), vjust=2, color="white", size=5) +
  geom_errorbar(aes(ymin=fractureTotal-se, ymax=fractureTotal+se), width=0.4, colour="grey", alpha=0.9, size=1)  +
  labs(x="",
       y="% of teams that fractured") + theme_classic() + theme(text = element_text(size=25),
        axis.text.x = element_text(size=16))
p
```

## Plot of total fracture percentages in the baseline condition:
# R baselinefracture
```{r, echo=TRUE}
groupedProportionFracture$fracture <- as.numeric(groupedProportionFracture$fracture)

resultsOverall <- groupedProportionFracture %>% filter(condition=="B") %>% group_by(n) %>%  summarise(count=n(),fracture=sum(fracture), percent=fracture/count, se=sqrt(percent*(1-percent)/count))
resultsOverall

baselineConsistency <- resultsOverall[1,]$percent^2 + (1-resultsOverall[1,]$percent)^2
baselineConsistency
```

# R baselinebyround
```{r, echo=TRUE}
resultsRound <- groupedProportionFracture %>% filter(condition=="B") %>% group_by(round) %>% summarise(n=n(),fracture=sum(fracture), notfracture=n()-fracture, percent=fracture/n, se=sqrt(percent*(1-percent)/n))
resultsRound

chisqinput <- subset(groupedProportionFracture, condition=="B")
chisqresults <- table(chisqinput$round, chisqinput$fracture)
chisqresults
chisq.test(chisqresults)

dat <- data.frame(roundFracturePercent= factor(c("Round 1","Round 2", "Round 3", "Round 4"), levels=c("Round 1","Round 2", "Round 3", "Round 4")),
                  fractureTotal = c(resultsRound$percent), se=c(resultsRound$se))
dat$fractureTotal <- round(dat$fractureTotal, 3)
p <- ggplot(data=dat, aes(x=roundFracturePercent, y=fractureTotal)) +
  geom_bar(stat="identity", fill="#2853C2", alpha=0.7)+
  geom_text(aes(label=fractureTotal), vjust=1.6, color="white", size=5)+
  scale_y_continuous(labels = scales::percent_format(10)) +
  geom_errorbar(aes(ymin=fractureTotal-se, ymax=fractureTotal+se), width=0.4, colour="grey", alpha=0.9, size=1) + theme_classic() + labs(y="% teams that fractured", x="") +
  theme(text = element_text(size=25),
        axis.text.x = element_text(size=12))
p
```

# Frequency of fracture proportions per condition:
```{r, echo=TRUE}
ggplot(groupedProportionFracture, aes(x = factor(fracture))) +
    geom_bar(fill="#2853C2", alpha=0.7, aes(y = (..count..)/sum(..count..))) +
scale_y_continuous(labels = scales::percent_format(10))  +
  scale_x_discrete(labels=c("0"="Keep this team", "1"="Do not keep this team")) + labs(y="% of total fracture scores", x="") +  facet_grid(.~results.condition) + theme_classic() + theme(text = element_text(size=25),
        axis.text.x = element_text(size=12))
```

## Frequency of fracture proportions per round:
```{r, echo=TRUE}
ggplot(groupedProportionFracture, aes(x = prop)) +
    geom_bar(fill="#2853C2", alpha=0.7, aes(y = (..count..)/sum(..count..))) +
  scale_y_continuous(labels = scales::percent_format(10))  + scale_x_continuous()+  labs(y="% of fracture proportions", x="Team fracture proportions") +  facet_grid(.~round) +  theme_classic() + theme(text = element_text(size=25),
        axis.text.x = element_text(size=16))
```

```{r, echo=TRUE, include=FALSE, eval=FALSE}
# Frequency of mean viability scores per condition:
## To-do: why are rows being removed, this isn't right:
ggplot(groupedProportionFracture, aes(x = factor(mean))) +
    geom_bar(fill="#2853C2", alpha=0.7, aes(y = (..count..)/sum(..count..))) +
scale_y_continuous(labels = scales::percent) +
  scale_x_discrete(limits=c("30", "50", "70")) +
     labs(subtitle="% of mean viability scores",
       x="range of means",
       y="frequency") + facet_grid(.~results.condition) +  theme_classic()
```

## Section #2: How often does fracture occur?

## CHI squared tests:
```{r, echo=TRUE}
## Test if whether fracture is independent of condition (i.e. baseline, control & treatment) at .05 significance level:
chi = table(groupedProportionFracture$results.condition, groupedProportionFracture$fracture)  
chi
print(chisq.test(chi))
```

## 2B: What's the overall % of fracturing the second time? (by condition)
```{r, echo=TRUE}
## Filtering second time only:
groupedProportionFracture$fracture <- as.numeric(groupedProportionFracture$fracture)
groupedProportionFractureOverall <- groupedProportionFracture %>%
      mutate(overallPercent = sum(as.numeric(fracture))) %>%
      summarise(n=n(), overallPercent=unique(overallPercent/n))  
mean(groupedProportionFractureOverall$overallPercent)

groupedProportionFractureB <- groupedProportionFracture %>%
      filter(condition=="B") %>%
      mutate(overallPercent = sum(as.numeric(fracture))) %>%
      summarise(n=n(), overallPercent=unique(overallPercent/n))  
print(groupedProportionFractureB)
mean(groupedProportionFractureB$overallPercent)

## To-do: review below code, worried it's incorrect:

groupedProportionFractureSecond <- groupedProportionFracture %>% group_by(results.condition) %>%
      filter(condition=="Ap") %>%
      mutate(overallPercent = sum(as.numeric(fracture))) %>%
      summarise(n=n(), overallPercent=unique(overallPercent)/n)
print(groupedProportionFractureSecond)

## For baseline theoretical distribution: (to-do: look over this, worried also that it's wrong)

groupedProportionFractureSecondBase <- groupedProportionFractureBaseline %>%
      filter(condition=="B") %>%
      summarise(n=n(), overallPercent=sum(as.numeric(fracture))/n)

print(groupedProportionFractureSecondBase$overallPercent)
```

## Proportion tests for total fracture change:
```{r, echo=TRUE}
## Set-up separate groups for proportion tests to answer: does unmasked fracture more/less than masked, and more/less than new pairs?

## Is the proportion of fracture in the second round significantly different in the two conditions (i.e. treatment + baseline)
treatmentvsBaselineChange <- c(48, 49)
propFractureChangeTreatmentvsBase <- prop.test(x = c(treatmentvsBaselineChange), n = c(100, 100))
print(propFractureChangeTreatmentvsBase)

## Is the proportion of fracture in the second round significantly different in the two conditions (i.e. control + baseline)
controlvsBaselineChange <- c(40, 49)
propFractureChangeControlvsBase <- prop.test(x = c(controlvsBaselineChange), n = c(100, 100))
print(propFractureChangeControlvsBase)
```

## Section 3: How consistent is fracture?

## 3A: calculating the conditional probabilities of fracture for each condition:
# R conditionaltreatment
```{r, echo=TRUE}
## If fractured the first time, what's the % of fracturing the second time? look at 1 and Ap combination for % in second time:
## Compare both treatment and control with baseline as theoretical distribution:
## Conditional probability for masked:
# of groups who fractured 1 and 2
treatmentFracture12 <- sum(ifelse(treatmentFracture1$fracture=="1" & treatmentFracture2$fracture=="1",1,0))/nrow(treatmentFracture)
# of groups who fractured only 1
treatmentFractureOnly1 <- sum(ifelse(treatmentFracture1$fracture=="1" & treatmentFracture2$fracture=="0",1,0))/nrow(treatmentFracture)
# of groups who fractured only 2
treatmentFractureOnly2 <- sum(ifelse(treatmentFracture1$fracture=="0" & treatmentFracture2$fracture=="1",1,0))/nrow(treatmentFracture)
# of groups who fractured never        
treatmentFractureNever <- sum(ifelse(treatmentFracture1$fracture=="0" & treatmentFracture2$fracture=="0",1,0))/nrow(treatmentFracture)
conditionalProbTreatment <- matrix(c(treatmentFracture12, treatmentFractureOnly1, treatmentFractureOnly2, treatmentFractureNever),ncol=2,byrow=TRUE)
colnames(conditionalProbTreatment) <- c("Ap frac","Ap no frac")
rownames(conditionalProbTreatment) <- c("A frac","A no frac")
conditionalProbTreatment <- as.table(conditionalProbTreatment)
print(conditionalProbTreatment)
```

# R conditionalcontrol
```{r, echo=TRUE}
## Conditional proability for unmasked:
# of groups who fractured 1 and 2
controlFracture12 <- sum(ifelse(controlFracture1$fracture=="1" & controlFracture2$fracture=="1",1,0))/nrow(controlFracture)
# of groups who fractured only 1
controlFractureOnly1 <- sum(ifelse(controlFracture1$fracture=="1" & controlFracture2$fracture=="0",1,0))/nrow(controlFracture)
# of groups who fractured only 2
controlFractureOnly2 <- sum(ifelse(controlFracture1$fracture=="0" & controlFracture2$fracture=="1",1,0))/nrow(controlFracture)
# of groups who fractured never        
controlFractureNever <- sum(ifelse(controlFracture1$fracture=="0" & controlFracture2$fracture=="0",1,0))/nrow(controlFracture)
conditionalProbControl <- matrix(c(controlFracture12, controlFractureOnly1, controlFractureOnly2, controlFractureNever),ncol=2,byrow=TRUE)
colnames(conditionalProbControl) <- c("Ap frac","Ap no frac")
rownames(conditionalProbControl) <- c("A frac","A no frac")
print(conditionalProbControl)
```

```{r, include=FALSE}
## Conditional proability for baseline
# of groups who fractured 1 and 2
# baselineFracture12 <- sum(ifelse(baselineFracture1$fracture=="1" & baselineFracture2$fracture=="1",1,0))/nrow(baselineFracture)
# # of groups who fractured only 1
# baselineFractureOnly1 <- sum(ifelse(baselineFracture1$fracture=="1" & baselineFracture2$fracture=="0",1,0))/nrow(baselineFracture)
# # of groups who fractured only 2
# baselineFractureOnly2 <- sum(ifelse(baselineFracture1$fracture=="0" & baselineFracture2$fracture=="1",1,0))/nrow(baselineFracture)
# # of groups who fractured never        
# baselineFractureNever <- sum(ifelse(baselineFracture1$fracture=="0" & baselineFracture2$fracture=="0",1,0))/nrow(baselineFracture)
# conditionalProbBaseline <- matrix(c(baselineFracture12, baselineFractureOnly1, baselineFractureOnly2, baselineFractureNever),ncol=2,byrow=TRUE)
# colnames(conditionalProbBaseline) <- c("Ap frac","Ap no frac")
# rownames(conditionalProbBaseline) <- c("A frac","A no frac")
# conditionalProbBaseline
```

```{r}
# kable(conditionalProbBaseline, "latex", caption = "Demo table", booktabs = T) %>%
# kable_styling(latex_options = c("striped", "hold_position"))
```

## 3B: Now investigating the big result: switch %: what's the % of pairs flipping their decisions?
# R consistencyprop
```{r, echo=TRUE}
## Convert format before merge: *this can be simplified*:
treatmentFracture2$fracture <- as.numeric(treatmentFracture2$fracture)
treatmentFracture1$fracture <- as.numeric(treatmentFracture1$fracture)
treatmentFracture$consistent <- treatmentFracture2$fracture == treatmentFracture1$fracture

controlFracture1$fracture <- as.numeric(controlFracture1$fracture)
controlFracture2$fracture <- as.numeric(controlFracture2$fracture)
controlFracture$consistent <- controlFracture2$fracture == controlFracture1$fracture

treatmentConsistentSum <- sum(treatmentFracture$consistent)
print(treatmentConsistentSum)
controlConsistentSum <- sum(controlFracture$consistent)
print(controlConsistentSum)

## Proportion test:
prop.test(x = c(treatmentConsistentSum, controlConsistentSum), n = c(nrow(treatmentFracture), nrow(controlFracture)))

allFracture <- rbind(treatmentFracture, controlFracture)
consistencyTable <- table(allFracture$results.condition, allFracture$consistent)
allFracture$results.condition <- factor(x=allFracture$results.condition, levels=c("control", "treatment"))
chisq.test(consistencyTable)
```

# R consistencylogit
```{r, echo=TRUE}
## Logistic regression because Chi-square needs more observations in each cell
consistencyLogit <- glm(data=allFracture, consistent ~ results.condition, family="binomial")
summary(consistencyLogit)
stargazer(consistencyLogit,
          covariate.labels = c("Masked (1: true)", "(Intercept)"),
          dep.var.labels=c("Consistent fracture"),
          no.space=TRUE,
          title="Consistency of fracture outcomes by condition. Masked teams decrease the log odds of a consistent outcome.",
          label="tab:consistency",
          #keep.stat="n",
          table.placement = "tb",
          star.cutoffs = c(0.05, 0.01, 0.001)
          )

## Chi goodness of fit:
## Using baseline as theoretical probability distribution
## Treatment:
#chisq.test(treatmentAbsChange, p = baselineAbsChange/sum(baselineAbsChange))
#chisq.test(treatmentAbsChange, controlAbsChange, p=baselineAbsChange)
## Control:
#chisq.test(controlAbsChange,p=baselineAbsChange)

prob <- predict(consistencyLogit, type=c("response"))
allFracture$prob <- prob

g <- roc(consistent ~ prob, data=allFracture, plot=TRUE, auc.polygon=TRUE, max.auc.polygon=TRUE, grid=TRUE,  print.auc=TRUE, show.thres=TRUE)
g

```

## Visualizing change:
# R consistencygraph
```{r, echo=TRUE}
normalizedControlConsistency <- controlConsistentSum /nrow(controlFracture)
normalizedTreatmentConsistency <- treatmentConsistentSum / nrow(treatmentFracture)
normalizedControlConsistencySe <- sqrt(normalizedControlConsistency*(1-normalizedControlConsistency)/nrow(controlFracture))
normalizedTreatmentConsistencySe <- sqrt(normalizedTreatmentConsistency*(1-normalizedTreatmentConsistency)/nrow(treatmentFracture))

## Visualize differences:
dat <- data.frame(FractureConsistency= factor(c("Masked","Unmasked"), levels=c("Masked","Unmasked")),
                  fractureValueSwitch = c(normalizedTreatmentConsistency, normalizedControlConsistency), SE=c(normalizedTreatmentConsistencySe, normalizedControlConsistencySe))

p <- ggplot(data=dat, aes(x=FractureConsistency, y=fractureValueSwitch)) +
  geom_bar(stat="identity", fill="#2853C2", alpha=0.7)+
  scale_y_continuous(labels = scales::percent_format(10)) +
  geom_errorbar(aes(ymin=c(normalizedTreatmentConsistency-normalizedTreatmentConsistencySe,
                          normalizedControlConsistency-normalizedControlConsistencySe),
                    ymax=c(normalizedTreatmentConsistency+normalizedTreatmentConsistencySe,
                           normalizedControlConsistency+normalizedControlConsistencySe)), width = 0.1) +
  geom_text(aes(label=sprintf("%1.0f%%", round(fractureValueSwitch, 2)*100)), vjust=4.6, color="white")+ #size=8)+
  theme_classic() + labs(x="",
       y="Percent of repeated\n collaborations with consistent\n fracture outcomes") + theme_classic()
  #theme(text = element_text(size=25),
  #      axis.text.x = element_text(size=16 )
  #      )
p
pdf('consistency.pdf', width=3.5, height=2.5)
p
dev.off();
```

## Visualizing meta-cognition differences:
# R metacognition
```{r}
# how accurate are they at guessing in general
accuracydf <- subset(individualProportionFracture, condition != "Ap")
chanceAccuracy <- sum(accuracydf$fracture == 0)/nrow(accuracydf)
chanceAccuracy
# how accurate would they be if they guessed their own opinion
ownaccuracy <- sum(accuracydf$blacklistIndividual == accuracydf$partnerFractured) / nrow(accuracydf)
ownaccuracy
# how accurate were they actually
accuracy <- sum(accuracydf$metaGuessedCorrectly) / nrow(accuracydf)
accuracy

# are they better than just stating their own opinion
prop.test(x = c(sum(accuracydf$blacklistIndividual == accuracydf$partnerFractured), sum(accuracydf$metaGuessedCorrectly)), n = c(nrow(accuracydf), nrow(accuracydf)))
# are they better than just guessing the most common outcome
prop.test(sum(accuracydf$metaGuessedCorrectly), nrow(accuracydf), chanceAccuracy)

metaAnswersSE <- sqrt(accuracy*(1-accuracy)/nrow(accuracydf))

# how consistent are their guesses
a <- subset(individualProportionFracture, condition == "A")
ap <- subset(individualProportionFracture, condition == "Ap")
joined <- a %>% inner_join(ap, by=c("id")) %>%
  filter(results.condition.x == "treatment") %>%
  select(id, results.condition.x, condition.x, condition.y, blacklistMeta.x, blacklistMeta.y, blacklistIndividual.x, blacklistIndividual.y)
joined$consistentGuess <- joined$blacklistMeta.x == joined$blacklistMeta.y
joined$consistentIndividual <- joined$blacklistIndividual.x == joined$blacklistIndividual.y
consistentGuessPercent <- sum(joined$consistentGuess) / nrow(joined)
consistentGuessPercent
consistentIndividualPercent <- sum(joined$consistentIndividual) / nrow(joined)
consistentIndividualPercent
prop.test(x = c(sum(joined$consistentGuess), sum(joined$consistentIndividual)), n = c(nrow(joined), nrow(joined)))

a <- subset(individualProportionFracture, condition == "A")
ap <- subset(individualProportionFracture, condition == "Ap")
joined <- a %>% inner_join(ap, by=c("id")) %>%
  filter(results.condition.x == "control") %>%
  select(id, results.condition.x, condition.x, condition.y, blacklistMeta.x, blacklistMeta.y, blacklistIndividual.x, blacklistIndividual.y)
joined$consistentGuess <- joined$blacklistMeta.x == joined$blacklistMeta.y
joined$consistentIndividual <- joined$blacklistIndividual.x == joined$blacklistIndividual.y
consistentGuessPercent <- sum(joined$consistentGuess) / nrow(joined)
consistentGuessPercent
consistentIndividualPercent <- sum(joined$consistentIndividual) / nrow(joined)
consistentIndividualPercent
prop.test(x = c(sum(joined$consistentGuess), sum(joined$consistentIndividual)), n = c(nrow(joined), nrow(joined)))

# ## Visualize differences:
# dat <- data.frame(fracturePrediction= factor(c("Correct fracture prediction"), levels=c("Correct fracture prediction")),
#                   fracturePredictionCorrect = c(metaAnswersCorrect), SE=c(metaAnswersSE))
#
# p <- ggplot(data=dat, aes(x=fracturePrediction, y=fracturePredictionCorrect)) +
#   geom_bar(stat="identity", fill="#2853C2", alpha=0.7)+
#   scale_y_continuous(labels = scales::percent_format(10)) +
#   geom_errorbar(aes(ymin=c(metaAnswersCorrect-metaAnswersSE),
#                     ymax=c(metaAnswersCorrect+metaAnswersSE), width = 0.1)) +
#   geom_text(aes(label=sprintf("%1.0f%%", round(fracturePredictionCorrect, 2)*100)), vjust=4.6, color="white")+ #size=8)+
#   theme_classic() + labs(x="",
#        y="Percent of individuals who accurately predicted \n \n partner's fracture score") + theme_classic()
#   #theme(text = element_text(size=25),
#   #      axis.text.x = element_text(size=16 )
#   #      )
# p
# pdf('metaPredictionQuestion.pdf', width=3.5, height=2.5)
# p
# dev.off();
```


## How much does individual predict fracture?
# R baddudes
```{r}
library(lme4)
library(lmerTest)
library(pROC)

didpartnerfracture <- individualProportionFracture %>%
  inner_join(individualProportionFracture, by = c("round", "batch", "room")) %>%
  filter(id.x != id.y, condition.x != "Ap") %>%
  select(id.x, id.y, partnerFractured.x, results.condition.x, condition.x)
numrounds <- didpartnerfracture %>%
  group_by(id.x) %>%
  summarise(count = n())
didpartnerfracture <- didpartnerfracture %>%
  inner_join(numrounds, by = c("id.x")) %>%
  filter(count >= 2)

didpartnerfracture$partnerFractured.x.logical <- as.logical(didpartnerfracture$partnerFractured.x)
didpartnerfracture$id.x <- as.factor(didpartnerfracture$id.x)
didpartnerfracture$results.condition.x <- as.factor(didpartnerfracture$results.condition.x)
personlogit <- glm(data = didpartnerfracture, partnerFractured.x ~ results.condition.x + id.x, family="binomial")
summary(personlogit)
prob <- predict(personlogit, type=c("response"))
didpartnerfracture$prob <- prob

reduced <- glm(data = didpartnerfracture, partnerFractured.x ~ results.condition.x, family="binomial")
reducedprob <- predict(reduced, type=c("response"))
didpartnerfracture$reducedprob <- reducedprob

g <- roc(partnerFractured.x ~ prob, data=didpartnerfracture,plot=TRUE, auc.polygon=TRUE, max.auc.polygon=TRUE, grid=TRUE,  print.auc=TRUE, show.thres=TRUE)
g

g <- roc(partnerFractured.x ~ reducedprob, data=didpartnerfracture,plot=TRUE, auc.polygon=TRUE, max.auc.polygon=TRUE, grid=TRUE,  print.auc=TRUE, show.thres=TRUE)
g


```


## Performance
```{r}
votes <- read.csv("ad performance - product performance.csv")
# rounds seem zero-indexed here
votes$round <- votes$round + 1
votes$room <- votes$team
votestats <- votes %>% group_by(product) %>%
  summarise(votemean = mean(score), votesd = sd(score), votecount=n())
votes <- votes %>% left_join(votestats, by="product") %>%
  mutate(zscore = (score-votemean)/votesd)

votecondition <- groupedProportionFracture %>%
  left_join(votes, by=c("round", "room", "batch")) %>%
  filter(!is.na(zscore)) %>%
  select(zscore, results.condition, fracture, condition, round, room, batch)

# Do fractured teams do worse than non-fractured teams?
t.test(zscore ~ fracture, data=votecondition)
```

```{r}
voteconsistency <- individualProportionFracture %>%
  inner_join(individualProportionFracture, by = c("id")) %>%
  filter(condition.x=="A", condition.y=="Ap") %>%
  select(condition.x, condition.y, id, fracture.x, fracture.y, results.condition.x, round.x, room.x, batch.x, room.y, round.y, batch.y) %>%
  left_join(votes, by=c("round.x" = "round", "room.x" = "room", "batch.x"=  "batch")) %>%
  left_join(votes, by=c("round.y" = "round", "room.y" = "room", "batch.y"=  "batch"), suffix=c(".x", ".y")) %>%
  filter(!is.na(zscore.x), !is.na(zscore.y)) %>%
  mutate(zdiff = abs(zscore.x - zscore.y))

voteconsistencysummary <- voteconsistency %>%
  summarise(by="results.condition.x", avg_zdiff = mean(zdiff), sd_zdiff=sd(zdiff))

t.test(zdiff ~ results.condition.x, data=voteconsistency)
```
