---
title: "Fracture CHI 2019 Results: n=2"
output: html_document
fig_width: 3.5
fig_caption: yes
---

## Set-up packages // libraries and prepare for data import: 
```{r echo=FALSE, include=FALSE, results='hide'}
## Uncomment install.packages and run outside of notebook environment: 
## install.packages(c("psych" ,"xtable", "tidyverse", "jsonlite", "likert", "ggplot2", "ploty", "mosaic", "modelr", "broom", "scales", "tinytex"))
library(psych)
library(likert)
library(jsonlite)
library(ggplot2)
library(plotly)
library(modelr)
library(broom)
library(scales)
library(tinytex)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(stargazer)
```

## Set-up directories, import and clean data: 
```{r, include=TRUE, echo=TRUE} 
rm(list=ls())
setwd("/Users/msb/Dropbox (Stanford HCI)/projects/asplode/bang/R") 
getwd()
dataPath = "../data"

## Function to extract blacklist surveys: 
extractBlacklistSurvey = function(frame,survey) {
  rounds = seq(1,4)
  roundResponses = lapply(rounds, function(round) {
    getCol = paste("results.",survey,".",round, sep="")
    surveyCols = Filter(function(x) grepl(getCol,x),names(frame))
    newCols = lapply(surveyCols, function(x) gsub(getCol,paste("results.",survey, sep=""),x) )
    surveyFrame = as.data.frame(frame[,surveyCols]) 
    if (is.null(newCols)) {return("No newCols")}
    names(surveyFrame) = newCols
    surveyFrame$id = frame$id
    surveyFrame$round = round
    surveyFrame$batch = frame$batch
    surveyFrame$rooms = frame$rooms
    surveyFrame$manipulationCheck <- frame$results.manipulationCheck
    surveyFrame$blacklist = frame$results.blacklistCheck
    return(surveyFrame)
  })
  return(Reduce(rbind, roundResponses))
}

#Find directory for import (be sure to verify that batch #s align from bangData import and imports below):
batches = dir(dataPath, pattern = "^[0-9]+$" )
completeBatches = Filter(function(batch) { 
  if (any(dir(paste(dataPath,batch,sep="/")) == "batch.json") && (any(dir(paste(dataPath,batch,sep="/")) == "users.json")) ) {
    batchData = read_json(paste(dataPath,batch,"batch.json",sep="/"), simplifyVector = TRUE)
    return(any(batchData$batchComplete == TRUE))
  } 
  return(FALSE)
}, batches)
## Debug: if you get error with flatten, you need to unload tidyverse in package column to the right:  
completeBatches <- as.numeric(completeBatches)
## To filter later on batch ##: 
options(scipen=999)
completeBatches = completeBatches[completeBatches>"1537366991708"]

userFiles = lapply(completeBatches, function(batch) {
  userFile = read_json(paste(dataPath,batch,"users.json",sep="/"), simplifyVector=TRUE)
  return(flatten(userFile, recursive = TRUE))
})
## Retroactively find rooms from chat data: 
overlappingFiles = Reduce(function(x,y) merge(x, y, all=TRUE), userFiles)
## Important: below is where you define the scope of your analysis, make sure this is set to include the right batches: 

overlappingFiles <- overlappingFiles %>% filter(batch>"1537366991708")

## Ignore weird batches: 
# overlappingFiles <- overlappingFiles %>% filter(batch!=1537389651302 | 1537392885929)

roundsWithRooms = apply(overlappingFiles,1,function(x) {
  roomsForIndividual = lapply(seq(1,4),function(y) {
    x$room = x$rooms[y]
    x$round = y
    return(x)
  })
  return(Reduce(rbind, roomsForIndividual))
})
```

```{r, include=FALSE}
## Libraries that we'll need but conflict with other stuff: 
library(tidyverse)
library(mosaic)
library(data.table)
library(car)
```

```{r, include=TRUE, echo=TRUE} 
## To filter the right batch numbers, add the first batch number for our runs (i.e. batch >= "first batch #") 
# overlappingFiles <- overlappingFiles %>% filter(batch=="1536335493362")

## Seperate viability function to deal with different column types 
extractViabilitySurvey = function(frame,survey) {
  rounds = seq(1,4)
  roundResponses = lapply(rounds, function(round) {
    getCol = paste("results.",survey,".",round, sep="")
    surveyCols = Filter(function(x) grepl(getCol,x),names(frame))
    newCols = lapply(surveyCols, function(x) gsub(getCol,paste("results.",survey, sep=""),x) )
    surveyFrame = as.data.frame(frame[,surveyCols]) 
    if (is.null(newCols)) {return("No newCols")}
    names(surveyFrame) = newCols
    surveyFrame$id = frame$id
    surveyFrame$round = round
    surveyFrame$batch = frame$batch
    surveyFrame$rooms = frame$rooms
    surveyFrame$manipulationCheck = frame$results.manipulationCheck
    surveyFrame$blacklist = frame$results.blacklistCheck
    return(surveyFrame)
    print(surveyFrame)
  dim(surveyFrame)
  })
  return(Reduce(bind_rows, roundResponses))
}
```

## More cleaning before visualizations: 
```{r, include=TRUE, echo=TRUE, message=FALSE} 
## Use extract survey function to reformat survey data: 
qFifteen <- extractBlacklistSurvey(overlappingFiles, 'qFifteenCheck')
qSixteen <- extractBlacklistSurvey(overlappingFiles, 'qSixteenCheck')
viabilitySurvey <- extractViabilitySurvey(overlappingFiles, 'viabilityCheck')
postSurveyQs <- cbind(qFifteen, qSixteen)
frame <- cbind(viabilitySurvey, postSurveyQs)
data <- frame[, !duplicated(colnames(frame))]
## Reduce to vertically combine rows in roundwithRooms list:  
finalRounds = as.data.frame(Reduce(rbind,roundsWithRooms))
## Subset incomplete cases from viability survey dataframe, use manipulation check b/c required for complete observation:
data <- data[data$manipulationCheck!="NULL",]
data <- data[data$manipulationCheck!="",]
##
data <- data[ , ! colnames(data) %in% c("manipulationCheck") ]
## Rename room to rooms so that both are retained in future merge: 
data <- rename(data, rooms = "rooms")
## Subset incomplete cases for final rounds dataframe: 
data2 <- finalRounds[finalRounds$results.manipulationCheck!="", ]
## Select only variables of interest from final rounds: 
data2 = data2 %>% select(id, batch, room, round, results.condition, results.format, results.manipulation, results.manipulationCheck)
## Convert to compatible data types before merge: 
data2 <- data2 %>% mutate(batch=unlist(batch), round=unlist(round), id=as.character(id), room=unlist(room)) 
data2 <- data2[data2$results.manipulationCheck!="NULL",]
data <- data %>% mutate(batch=unlist(batch), id=as.character(id), round=unlist(round))  
## Before merge, data and data2 should have the same # of observations
## Merge columns by id, round and batch #s: 
data <- full_join(data, data2, by=NULL)
## Check what this error is: 
## Subset only observations with batch #s in complete batches 
allConditions <- data[data$batch %in% completeBatches, ]
## Convert unique names: 
data <- data[, !duplicated(colnames(data))]
```
## Conditionally assign conditions based on treatment and results column: 
```{r, echo=TRUE} 
## Messy, but robust? Verify, verify, verify people:   
## For runs with 4 rounds: 
data <- data %>% mutate(
  condition = case_when(
    results.format=="c(1, 1, 2, 3)" & round==1 ~ "A", 
    results.format=="c(1, 1, 2, 3)" & round==2 ~ "Ap", 
    results.format=="c(1, 1, 2, 3)" & round==3 ~ "B", 
    results.format=="c(1, 1, 2, 3)" & round==4 ~ "B", 
    results.format=="c(1, 2, 1, 3)" & round==1 ~ "A", 
    results.format=="c(1, 2, 1, 3)" & round==2 ~ "B", 
    results.format=="c(1, 2, 1, 3)" & round==3 ~ "Ap", 
    results.format=="c(1, 2, 1, 3)" & round==4 ~ "B", 
    results.format=="c(2, 1, 1, 3)" & round==1 ~ "B", 
    results.format=="c(2, 1, 1, 3)" & round==2 ~ "A", 
    results.format=="c(2, 1, 1, 3)" & round==3 ~ "Ap", 
    results.format=="c(2, 1, 1, 3)" & round==4 ~ "B", 
    results.format=="c(2, 3, 1, 1)" & round==1 ~ "B", 
    results.format=="c(2, 3, 1, 1)" & round==2 ~ "B", 
    results.format=="c(2, 3, 1, 1)" & round==3 ~ "A", 
    results.format=="c(2, 3, 1, 1)" & round==4 ~ "Ap",
    results.format=="c(2, 1, 3, 1)" & round==1 ~ "B", 
    results.format=="c(2, 1, 3, 1)" & round==2 ~ "A", 
    results.format=="c(2, 1, 3, 1)" & round==3 ~ "B", 
    results.format=="c(2, 1, 3, 1)" & round==4 ~ "Ap", 
    results.format=="c(1, 2, 3, 1)" & round==1 ~ "A", 
    results.format=="c(1, 2, 3, 1)" & round==2 ~ "B", 
    results.format=="c(1, 2, 3, 1)" & round==3 ~ "B", 
    results.format=="c(1, 2, 3, 1)" & round==4 ~ "Ap"
  )) 
```

```{r, echo=TRUE}
## Rename Q15 + Q16: 
data <- data %>% rename("blacklistIndividual"=results.qFifteenCheck) %>% rename("blacklistMeta"=results.qSixteenCheck) 
## Factor for visualizations: 
levels <- c("Strongly Disagree", "Disagree", "Neutral","Agree", "Strongly Agree") 
clean <- data %>% 
  mutate_at(.vars = vars(contains("results.viabilityCheck")), funs(factor(., levels = levels))) %>% 
  mutate(blacklistIndividual = as.character(blacklistIndividual), blacklistMeta = as.character(blacklistMeta))
          
## Create a new dataframe that converts factors to numeric for statistical analyses:
stats <- clean %>% mutate_if(is.factor, as.numeric)
for (i in 1:nrow(stats)) {
  stats$sum[i] <- sum(stats[i,1:14])                          
} 

## Revalue repeat team: keep plyr b/c some weird R stuff requires library to be called directly (recode values to )
## stats$blacklistIndividual <- car::recode(stats$blacklistIndividual, "1=0;2=1") 
## stats$blacklistMeta <- car::recode(stats$blacklistMeta, "1=0;2=1") 

## Mutate to add stats columns and change format type: 
stats <- stats %>% 
  mutate(median = median(sum), mean = mean(sum), room = unlist(room), results.condition = unlist(results.condition), results.format=as.character(results.format), blacklistIndividual)

## Simplify by only selecting specific variables of interest: 
stats <- stats %>% select(contains("results.viabilityCheck"), id, round, batch, batch, room, blacklistIndividual, blacklistMeta, results.manipulation, results.condition, results.manipulationCheck, results.format, condition, sum, median, mean)

stats$blacklistMeta <- plyr::revalue(stats$blacklistMeta, c("Keep this team"="0", "Do not keep this team"="1"))
stats$blacklistIndividual <- plyr::revalue(stats$blacklistIndividual, c("Keep this team"="0", "Do not keep this team"="1"))
stats$blacklistIndividual <- as.numeric(stats$blacklistIndividual)
stats$blacklistMeta <- as.numeric(stats$blacklistMeta)

groupedProportion <- stats %>%
  group_by(room, batch, round, condition, results.condition, results.format) %>%  ## to-do: add group ID in storage db. 
  summarise(n=n(), mean=mean(sum), median=median(sum), prop=sum(blacklistIndividual)/n) %>% 
## Filter out all teams with n=1 (i.e. a person in a one person team) 
  filter(n==2)
print(groupedProportion)
## Individual proportion: 
individualProportion <- stats %>% group_by(round, batch, room) %>% 
  mutate(sum=sum, mean=mean(sum), median=median(sum), n=n(),prop=sum(blacklistIndividual)/n) %>% 
  filter(n==2)
print(individualProportion)

## Table showing how many teams we've run in each condition combination:  
print(table(groupedProportion$condition, groupedProportion$results.condition)) 
```

## Probability of fracture across teams and condition combinations: 
```{r, echo=TRUE}
## Define and initialize cut-off point for fracture: 
groupedProportionFracture <- groupedProportion %>%
  group_by(results.condition, condition) %>% 
  mutate(fracture = case_when (prop<.50 ~ "0", 
                                prop>=.50~ "1"), sd=sd(fracture)) 

## Define and initialize cut-off point for fracture: 
individualProportionFracture <- individualProportion %>%
  group_by(results.condition, condition) %>% 
  mutate(fracture = case_when (prop<.50 ~ "0", 
                                prop>=.50~ "1"), sd=sd(fracture)) 

individualProportionFracture$partnerFractured <- ifelse(individualProportionFracture$prop == 0, FALSE,
                                                        ifelse(individualProportionFracture$prop == 1, TRUE, 
                                       ifelse(individualProportionFracture$blacklistIndividual == 0, TRUE, FALSE)))

individualProportionFracture$metaGuessedCorrectly <- individualProportionFracture$blacklistMeta == individualProportionFracture$partnerFractured

## Baseline: (we probably won't need this since we are artificially making baseline conditions)
# groupedProportionFractureBaseline <- 
#   groupedProportionFracture %>% 
# filter(results.condition=="baseline") %>% 
#   filter(id %in% condition=="A" & condition=="C")
# baselineFracture1 <- groupedProportionFractureBaseline %>% filter(condition=="A")
# baselineFracture2 <- groupedProportionFractureBaseline %>% filter(condition=="C")

# To-do: triple check if this is right:  

groupedProportionFractureBaseline <- groupedProportionFracture %>% filter(results.format=="c(1, 1, 2, 3)" | results.format=="c(1, 2, 1, 3)" | results.format=="c(2, 1, 1, 3)" | results.format=="c(2, 3, 1, 1)" | results.format=="c(2, 1, 3, 1)") %>% filter(round=="1" | round=="4") 
baselineFracture1 <- groupedProportionFractureBaseline %>% filter(round=="1")
baselineFracture2 <- groupedProportionFractureBaseline %>% filter(round=="4")
##baselineFracture1$fracture1 <- baselineFracture1$fracture
## baselineFracture2$fracture2 <- baselineFracture2$fracture
## To deal with unequal round 1 and round 4 # of teams, only joins if attributes are present in both columns: 
## baselineFracture2 <- baselineFracture2 %>% semi_join(baselineFracture1, by = c("results.format", "batch"))

## Treatment: 
groupedProportionFractureTreatment <- groupedProportionFracture %>% 
filter(results.condition=="treatment")
treatmentFracture1 <- groupedProportionFractureTreatment %>% filter(condition=="A")
treatmentFracture2 <- groupedProportionFractureTreatment %>% filter(condition=="Ap")
## To deal with unequal round # of teams: 
treatmentFracture1 <- treatmentFracture1 %>% semi_join(treatmentFracture2, by=c("results.format", "batch", "n"))
treatmentFracture <- cbind(treatmentFracture1, treatmentFracture2)

## Control:  
groupedProportionFractureControl <- groupedProportionFracture %>% 
  filter(results.condition=="control") 
controlFracture1 <- groupedProportionFractureControl %>% filter(condition=="A")
controlFracture2 <- groupedProportionFractureControl %>% filter(condition=="Ap")
## To deal with unequal round # of teams: 
controlFracture2 <- controlFracture2 %>% semi_join(controlFracture2, by=c("results.format", "batch", "condition"))
controlFracture <- cbind(controlFracture1, controlFracture2)

## Manipulation check: 
## Use individual proportion data frame b/c we're interested in looking at individuals that were in teams >n=1
teamPatterns <- "Team 1 and Team 2|Team 2 and Team 3|Team 3 and Team 4|Team 1 and Team 3|Team 1 and Team 4|Team 2 and Team 4"
individualProportion$manipulationAnswerKey <- str_extract(individualProportion$results.manipulation,teamPatterns) 
individualProportion$manipulationAnswers <- individualProportion$results.manipulationCheck
individualProportion$results.condition = unlist(individualProportion$results.condition)
## Omit NAs and results that can't be processed: 
cleanManipulation <- individualProportion[with(individualProportion, grepl(teamPatterns, manipulationAnswers) & grepl(teamPatterns, manipulationAnswerKey)),]
## Transform into compatiable form: 
cleanManipulation$manipulationAnswers = unlist(cleanManipulation$manipulationAnswers)
```

## Section #1: Does fracture have continuity with prior measures?

## 1A: Report the % of correct guesses on the manipulation check: 
```{r}
## Subset just one observation per person (right now there are four b/c rounds)
## cleanManipulation <- cleanManipulation[!duplicated(cleanManipulation$id),]

## Treatment manipulation ## need to figure out why filter doesn't work here. 
treatmentManipulation <- cleanManipulation %>%  filter(results.condition=="treatment")
## Each user has three observations, we really just need one for manipulation: 
treatmentManipulation <- unique(setDT(treatmentManipulation), by = c('id')) 

## If user manipulation answers == manipulation answer key then add 1 
treatmentManipulation$correctAnswer <- treatmentManipulation$manipulationAnswers==treatmentManipulation$manipulationAnswerKey
treatmentManipulation$correctAnswers <- sum(ifelse(treatmentManipulation$manipulationAnswers==treatmentManipulation$manipulationAnswerKey,1,0))
## Calculate percent of correct manipulation answers for treatment: 
treatmentManipulation <- treatmentManipulation %>% mutate(percentCorrect = (correctAnswers/(nrow(treatmentManipulation))))
graphTreatment <- unique(round(treatmentManipulation$percentCorrect, 2))

## Control manipulation: 
controlManipulation <- cleanManipulation %>% filter(results.condition=="control") 
controlManipulation <- unique(setDT(controlManipulation), by = c('id')) 

## If user manipulation answers == manipulation answer key then add 1 
controlManipulation$correctAnswer <- controlManipulation$manipulationAnswers==controlManipulation$manipulationAnswerKey
controlManipulation$correctAnswers <- sum(ifelse(controlManipulation$manipulationAnswers==controlManipulation$manipulationAnswerKey,1,0))
## Calculate percent of correct manipulation answers for control: 
controlManipulation <- controlManipulation %>% mutate(percentCorrect = (correctAnswers/(nrow(controlManipulation))))
graphControl <- unique(round(controlManipulation$percentCorrect, 2))

treatmentTotal <- sum(treatmentManipulation$correctAnswer)
controlTotal <- sum(controlManipulation$correctAnswer)
controlManipulation2 <- unique(controlManipulation$percentCorrect)*100
treatmentManipulation2 <- unique(treatmentManipulation$percentCorrect)*100
chanceManipulation <- c(1/6*100)
print(c(controlManipulation2, treatmentManipulation2, chanceManipulation))

treatmentSE <- sqrt((treatmentTotal/nrow(treatmentManipulation) * (1 - (treatmentTotal/nrow(treatmentManipulation))))/nrow(treatmentManipulation))
```
## Plot for manipulation check results:
# R manipulationcheck
```{r, echo=TRUE}
dat <- data.frame(manipulationCheck=factor(c("Masked condition"), levels=c("Masked condition")),
                  manipulation = c(graphTreatment))

p <- ggplot(data=dat, aes(x=manipulationCheck, y=manipulation)) +
  geom_bar(stat="identity", fill="#2853C2", alpha=.7)+
  geom_hline(yintercept=1/6, size=1, color="grey") +   
  geom_errorbar(aes(ymin=manipulation-treatmentSE, ymax=manipulation+treatmentSE), width = 0.1)+
  #geom_text(aes(label=manipulation), vjust=1.6, color="white", size=5)+
  scale_y_continuous(labels = scales::percent_format(1)) + 
  theme_classic() + labs(subtitle="", 
       x="",
       y="Accuracy at identifying\n the repeat collaborators") +
  #theme(text = element_text(size=22), axis.text.x = element_text(size=22))

pdf('manipulationcheck.pdf', width=3.5, height=2.5)
p
dev.off();
p
```

## 1B: Proportion test comparing treatment manipulation percent correct with chance: 
# R manipulationcheckprop
```{r}
## Proportion test with treatment and chance: 
treatmentChanceManipulation <- prop.test(treatmentTotal, nrow(treatmentManipulation), chanceManipulation/100)
#prop.test(x = c(chanceManipulation, treatmentManipulation2), n = c(100, 100))
print(treatmentChanceManipulation)

## Proportion test with treatment and control: 
treatmentControlManipulation <- prop.test(controlTotal, nrow(controlManipulation), chanceManipulation/100)
#prop.test(x = c(controlManipulation2, chanceManipulation), n = c(100, 100))
print(treatmentControlManipulation)
```

## 1C: Logistic regression predicting binary fracture outcome from viability scales: 
# R viabilitydescriptive
```{r}
viabilityDescriptive <- describe(groupedProportionFracture$mean)
viabilityDescriptive

```

# R viabilitycheck
```{r}
describe(subset(groupedProportionFracture, logicalfracture == TRUE)$mean)
describe(subset(groupedProportionFracture, logicalfracture == FALSE)$mean)
t.test(groupedProportionFracture$mean ~ groupedProportionFracture$logicalfracture)

## Simple logistic regression: we will fit a logistic regression model in order to predict 
## the probability of fracture based on a team's average viability sum: 
groupedProportionFracture$fracture <- as.numeric(groupedProportionFracture$fracture)
groupedProportionFracture$logicalfracture <- as.logical(groupedProportionFracture$fracture)
model1 <- glm(logicalfracture ~ mean, family = "binomial", data = groupedProportionFracture)
stargazer(model1,
          covariate.labels = c("Average viability scale", "(Intercept)"),
          dep.var.labels=c("Fracture"), 
          no.space=TRUE, 
          title="The relationship between the viability scale and fracture. Higher viability was significantly associated with lower log odds of fracture.", 
          label="tab:viability", 
          #keep.stat="n",
          table.placement = "tb",
          star.cutoffs = c(0.05, 0.01, 0.001)
          )

summary(model1)

exp(cbind(coef(model1), confint(model1)))
```

## Test predictive power of logistic regression: 
```{r, include=FALSE, }
## From output we see that a one unit decrease in mean viability score is associated with a decreasein the log odds of fracture by 0.26 units. 

## Check predictive power: 

## Split data into 60% training and 40% testing data sets to test how well the model performs 
set.seed(123)
groupedProportionFracture$fracture <- as.numeric(groupedProportionFracture$fracture) 
sample <- sample(c(TRUE, FALSE), nrow(groupedProportionFracture), replace = T, prob = c(0.6,0.4))
train <- groupedProportionFracture[sample, ]
test <- groupedProportionFracture[!sample, ]

model2 <- glm(fracture ~ mean, family = "binomial", data = train)
stargazer(model2, title="Training Results", align=TRUE)
summary(model2)
print(model2)
## To assess the linear regression deviance, look at deviance in summary output, if 
## deviance == sum of sqaures in linear regression, null deviance == difference between. a model with only the intercept ("no mean predictors") and the a saturated model a model with a theoretically perfect fit. Model deviance (residual deviance) should be lower (i.e. small values == better fit). 

print(tidy(model1)) 
print(tidy(model2))
## Coefficient estimtes from log regression characterize relationship between the predictor and 
## response variable on a log-odds scale, so binary increase from no fracture - fracture can be interpreted as associated with a decrease in mean viability sum. 

## More coefficient output: measure the confidence intervals and accuracy of the coefficent: 
confint(model1)

## Making predictions: 
## What is the probability of fracture given the following team mean viability scores: for example purposes: 55 and 65: 

predict(model2, data.frame(mean = c(55, 65)), type = "response")

## From the output, we can see that the probability of fracture decreases from 0.31% to 0.03% when mean viability sum increases from 55 to 65. 

## Another example, with means 45 and 60: 

predict(model2, data.frame(mean = c(40, 60)), type = "response")

## From the output, we can see that the probability of fracture decreases from 0.96% to 0.10% when mean viability sum increases from 40 to 60. 

## Model evaluation & diagnostics: 
## How well does the model fit the data? And how accurate are the predictions on an out-of-sample data set?

## Residul assessment: 
model1_data <- augment(model1) %>% 
  mutate(index = 1:n())

ggplot(model1_data, aes(index, .std.resid, color = mean)) + 
  geom_point(alpha = .5) +
  geom_ref_line(h = 3)

## Validation of predicted values: 
## How well does the model perform when predicting the target variable on out-of-sample observations? 

test.predicted.m1 <- predict(model1, newdata = test, type = "response")

## Classification performance for each model on the test data. Output gives us a list of true / false positives: 

list(
  model1 = table(test$mean, test.predicted.m1 > 0.5) %>% prop.table() %>% round(3)) 

table(test$mean, test.predicted.m1 > 0.5)
```

```{r, include=FALSE, eval=FALSE}
## Logistic regression on individual score: 
individualProportionFractureTreatment <- individualProportionFracture %>% 
filter(results.condition=="treatment")
individualTreatmentFracture1 <- individualProportionFractureTreatment %>% filter(condition=="A")
individualTreatmentFracture2 <- individualProportionFractureTreatment %>% filter(condition=="Ap")
individualTreatmentFracture <- cbind(individualTreatmentFracture1, individualTreatmentFracture2)
## Need to finish this 
```

## 1D: Graph of fracture/no fracture vs. mean/stdev viability scale

## Boxplot: mean viability survey scores + fracture value (group level + individual level)
# R viabilityplot
```{r, include=TRUE, echo=TRUE}
g <- ggplot(groupedProportionFracture, aes(factor(fracture), mean)) +
  geom_boxplot(varwidth=T, fill="#2853C2", alpha=0.7) + 
  labs( 
       x="",
       y="Average viability score") +
  scale_x_discrete(labels=c("0" = "No fracture", "1" = "Fracture")) + theme_classic()
  #theme(text = element_text(size=25), axis.text.x = element_text(size=16))
pdf('viabilityplot.pdf', width=3.5, height=2)
g
dev.off();

g <- ggplot(individualProportionFracture, aes(factor(fracture), sum)) 
g + geom_boxplot(varwidth=T, fill="#2853C2", alpha=0.7) + 
  labs(x="",
       y="Individual viability score") +
 scale_x_discrete(labels=c("0" = "Keep this team", "1" = "Do not keep this team")) + theme_classic() + theme(text = element_text(size=25),
        axis.text.x = element_text(size=16))

```

```{r, include=FALSE, eval=FALSE}
## Correlation scatterplot: mean viability survey scores + fracture value (group level + individual level)
## Grouped fracture correlation: 
ggplot(data=groupedProportionFracture, aes(fracture, mean)) + 
   geom_point() +
  stat_smooth(method = "lm", col = "red") + labs(title="Scatterplot correlation between teams' mean viability and binary fracture scores", y="Teams' mean viability survey score (range 14-70) ", x="Teams' binary fracture score") + 
scale_x_discrete(labels=c("0" = "Keep this team", "1" = "Do not keep this team"))

## Individual fracture correlation: 
ggplot(data=individualProportionFracture, aes(fracture, mean)) + 
   geom_point() +
  stat_smooth(method = "lm", col = "red") + labs(subtitle="Scatterplot correlation between individuals' mean viability and binary fracture scores", y="Individual mean viability survey scores (range 14-70) ", x="Individual binary fracture score") +
scale_x_discrete(labels=c("0" = "Keep this team", "1" = "Do not keep this team"))

## Grouped fracture proportion correlation: 
ggplot(data=individualProportionFracture, aes(prop, mean)) + 
   geom_point() +
  stat_smooth(method = "lm", col = "red") + labs(subtitle="Scatterplot correlation between teams' mean viability and team fracture proportion", y="Individual mean viability survey scores (range 14-70 ", x="Teams' fracture proportion") + 
scale_x_continuous(labels=c("0" = "Keep this team", "0.40", "0.60", "0.80" ,"1.00" = "Do not keep this team"))
```

## Group by and summarise fracture percentage by condition + plot for percentages:
```{r, echo=TRUE}
resultsPercent <- groupedProportionFracture %>% group_by(results.condition) %>% summarise(n=n(), fracture=sum(fracture), percent=fracture/n, se=sqrt(percent*(1-percent)/n)) %>% filter(results.condition=="control" | results.condition=="treatment")
dat <- data.frame(conditionFracturePercent= factor(c("Unmasked","Masked"), levels=c("Unmasked","Masked")),
                  fractureTotal = c(resultsPercent$percent), se=c(resultsPercent$se))  
dat$fractureTotal <- round(dat$fractureTotal, 3)

p <- ggplot(data=dat, aes(x=conditionFracturePercent, y=fractureTotal)) +
  geom_bar(stat="identity", fill="#2853C2", alpha=0.7)+
  scale_y_continuous(labels = scales::percent_format(10)) + 
  geom_text(aes(label=fractureTotal), vjust=2, color="white", size=5) +
  geom_errorbar(aes(ymin=fractureTotal-se, ymax=fractureTotal+se), width=0.4, colour="grey", alpha=0.9, size=1)  + 
  labs(x="",
       y="% of teams that fractured") + theme_classic() + theme(text = element_text(size=25),
        axis.text.x = element_text(size=16))
p
```

## Plot of total fracture percentages in the baseline condition: 
# R baselinefracture
```{r, echo=TRUE}
groupedProportionFracture$fracture <- as.numeric(groupedProportionFracture$fracture) 

resultsOverall <- groupedProportionFracture %>% filter(condition=="B") %>% group_by(n) %>%  summarise(count=n(),fracture=sum(fracture), percent=fracture/count, se=sqrt(percent*(1-percent)/count)) 
resultsOverall

baselineConsistency <- resultsOverall[1,]$percent^2 + (1-resultsOverall[1,]$percent)^2
baselineConsistency
```

# R baselinebyround
```{r, echo=TRUE}
resultsRound <- groupedProportionFracture %>% filter(condition=="B") %>% group_by(round) %>% summarise(n=n(),fracture=sum(fracture), notfracture=n()-fracture, percent=fracture/n, se=sqrt(percent*(1-percent)/n)) 
resultsRound

chisqinput <- subset(groupedProportionFracture, condition=="B")
chisqresults <- table(chisqinput$round, chisqinput$fracture)
chisqresults
chisq.test(chisqresults)

dat <- data.frame(roundFracturePercent= factor(c("Round 1","Round 2", "Round 3", "Round 4"), levels=c("Round 1","Round 2", "Round 3", "Round 4")),
                  fractureTotal = c(resultsRound$percent), se=c(resultsRound$se))
dat$fractureTotal <- round(dat$fractureTotal, 3)
p <- ggplot(data=dat, aes(x=roundFracturePercent, y=fractureTotal)) +
  geom_bar(stat="identity", fill="#2853C2", alpha=0.7)+
  geom_text(aes(label=fractureTotal), vjust=1.6, color="white", size=5)+
  scale_y_continuous(labels = scales::percent_format(10)) + 
  geom_errorbar(aes(ymin=fractureTotal-se, ymax=fractureTotal+se), width=0.4, colour="grey", alpha=0.9, size=1) + theme_classic() + labs(y="% teams that fractured", x="") + 
  theme(text = element_text(size=25),
        axis.text.x = element_text(size=12)) 
p
```

# Frequency of fracture proportions per condition: 
```{r, echo=TRUE}
ggplot(groupedProportionFracture, aes(x = factor(fracture))) + 
    geom_bar(fill="#2853C2", alpha=0.7, aes(y = (..count..)/sum(..count..))) +
scale_y_continuous(labels = scales::percent_format(10))  + 
  scale_x_discrete(labels=c("0"="Keep this team", "1"="Do not keep this team")) + labs(y="% of total fracture scores", x="") +  facet_grid(.~results.condition) + theme_classic() + theme(text = element_text(size=25),
        axis.text.x = element_text(size=12)) 
```

## Frequency of fracture proportions per round: 
```{r, echo=TRUE}
ggplot(groupedProportionFracture, aes(x = prop)) + 
    geom_bar(fill="#2853C2", alpha=0.7, aes(y = (..count..)/sum(..count..))) +
  scale_y_continuous(labels = scales::percent_format(10))  + scale_x_continuous()+  labs(y="% of fracture proportions", x="Team fracture proportions") +  facet_grid(.~round) +  theme_classic() + theme(text = element_text(size=25),
        axis.text.x = element_text(size=16)) 
```

```{r, echo=TRUE, include=FALSE, eval=FALSE}
# Frequency of mean viability scores per condition: 
## To-do: why are rows being removed, this isn't right: 
ggplot(groupedProportionFracture, aes(x = factor(mean))) + 
    geom_bar(fill="#2853C2", alpha=0.7, aes(y = (..count..)/sum(..count..))) +
scale_y_continuous(labels = scales::percent) + 
  scale_x_discrete(limits=c("30", "50", "70")) + 
     + labs(subtitle="% of mean viability scores", 
       x="range of means",
       y="frequency") + facet_grid(.~results.condition) +  theme_classic()
```

## Section #2: How often does fracture occur?

## CHI squared tests: 
```{r, echo=TRUE}
library(MASS)  
## Test if whether fracture is independent of condition (i.e. baseline, control & treatment) at .05 significance level: 
chi = table(groupedProportionFracture$results.condition, groupedProportionFracture$fracture)  
chi
print(chisq.test(chi)) 
```

## 2B: What's the overall % of fracturing the second time? (by condition)
```{r, echo=TRUE}
## Filtering second time only: 
groupedProportionFracture$fracture <- as.numeric(groupedProportionFracture$fracture)
groupedProportionFractureOverall <- groupedProportionFracture %>% 
      mutate(overallPercent = sum(as.numeric(fracture))) %>% 
      summarise(n=n(), overallPercent=unique(overallPercent/n))  
mean(groupedProportionFractureOverall$overallPercent)

groupedProportionFractureB <- groupedProportionFracture %>% 
      filter(condition=="B") %>% 
      mutate(overallPercent = sum(as.numeric(fracture))) %>% 
      summarise(n=n(), overallPercent=unique(overallPercent/n))  
print(groupedProportionFractureB) 
mean(groupedProportionFractureB$overallPercent)

## To-do: review below code, worried it's incorrect: 

groupedProportionFractureSecond <- groupedProportionFracture %>% group_by(results.condition) %>% 
      filter(condition=="Ap") %>% 
      mutate(overallPercent = sum(as.numeric(fracture))) %>% 
      summarise(n=n(), overallPercent=unique(overallPercent)/n) 
print(groupedProportionFractureSecond)

## For baseline theoretical distribution: (to-do: look over this, worried also that it's wrong)

groupedProportionFractureSecondBase <- groupedProportionFractureBaseline %>%
      filter(condition=="B") %>% 
      summarise(n=n(), overallPercent=sum(as.numeric(fracture))/n) 

print(groupedProportionFractureSecondBase$overallPercent)
```

## Proportion tests for total fracture change: 
```{r, echo=TRUE}
## Set-up separate groups for proportion tests to answer: does unmasked fracture more/less than masked, and more/less than new pairs? 

## Is the proportion of fracture in the second round significantly different in the two conditions (i.e. treatment + baseline) 
treatmentvsBaselineChange <- c(48, 49)
propFractureChangeTreatmentvsBase <- prop.test(x = c(treatmentvsBaselineChange), n = c(100, 100))
print(propFractureChangeTreatmentvsBase) 

## Is the proportion of fracture in the second round significantly different in the two conditions (i.e. control + baseline) 
controlvsBaselineChange <- c(40, 49)
propFractureChangeControlvsBase <- prop.test(x = c(controlvsBaselineChange), n = c(100, 100))
print(propFractureChangeControlvsBase)
```

## Section 3: How consistent is fracture? 

## 3A: calculating the conditional probabilities of fracture for each condition: 
# R conditionaltreatment
```{r, echo=TRUE}
## If fractured the first time, what's the % of fracturing the second time? look at 1 and Ap combination for % in second time: 
## Compare both treatment and control with baseline as theoretical distribution: 
## Conditional probability for masked: 
# of groups who fractured 1 and 2
treatmentFracture12 <- sum(ifelse(treatmentFracture1$fracture=="1" & treatmentFracture2$fracture=="1",1,0))/nrow(treatmentFracture)
# of groups who fractured only 1
treatmentFractureOnly1 <- sum(ifelse(treatmentFracture1$fracture=="1" & treatmentFracture2$fracture=="0",1,0))/nrow(treatmentFracture) 
# of groups who fractured only 2
treatmentFractureOnly2 <- sum(ifelse(treatmentFracture1$fracture=="0" & treatmentFracture2$fracture=="1",1,0))/nrow(treatmentFracture)
# of groups who fractured never        
treatmentFractureNever <- sum(ifelse(treatmentFracture1$fracture=="0" & treatmentFracture2$fracture=="0",1,0))/nrow(treatmentFracture)
conditionalProbTreatment <- matrix(c(treatmentFracture12, treatmentFractureOnly1, treatmentFractureOnly2, treatmentFractureNever),ncol=2,byrow=TRUE)
colnames(conditionalProbTreatment) <- c("Ap frac","Ap no frac") 
rownames(conditionalProbTreatment) <- c("A frac","A no frac")
conditionalProbTreatment <- as.table(conditionalProbTreatment)
print(conditionalProbTreatment) 
```

# R conditionalcontrol
```{r, echo=TRUE}
## Conditional proability for unmasked: 
# of groups who fractured 1 and 2
controlFracture12 <- sum(ifelse(controlFracture1$fracture=="1" & controlFracture2$fracture=="1",1,0))/nrow(controlFracture)
# of groups who fractured only 1
controlFractureOnly1 <- sum(ifelse(controlFracture1$fracture=="1" & controlFracture2$fracture=="0",1,0))/nrow(controlFracture) 
# of groups who fractured only 2
controlFractureOnly2 <- sum(ifelse(controlFracture1$fracture=="0" & controlFracture2$fracture=="1",1,0))/nrow(controlFracture)
# of groups who fractured never        
controlFractureNever <- sum(ifelse(controlFracture1$fracture=="0" & controlFracture2$fracture=="0",1,0))/nrow(controlFracture)
conditionalProbControl <- matrix(c(controlFracture12, controlFractureOnly1, controlFractureOnly2, controlFractureNever),ncol=2,byrow=TRUE)
colnames(conditionalProbControl) <- c("Ap frac","Ap no frac") 
rownames(conditionalProbControl) <- c("A frac","A no frac")
print(conditionalProbControl) 
```

```{r, include=FALSE}
## Conditional proability for baseline
# of groups who fractured 1 and 2
# baselineFracture12 <- sum(ifelse(baselineFracture1$fracture=="1" & baselineFracture2$fracture=="1",1,0))/nrow(baselineFracture)
# # of groups who fractured only 1
# baselineFractureOnly1 <- sum(ifelse(baselineFracture1$fracture=="1" & baselineFracture2$fracture=="0",1,0))/nrow(baselineFracture)
# # of groups who fractured only 2
# baselineFractureOnly2 <- sum(ifelse(baselineFracture1$fracture=="0" & baselineFracture2$fracture=="1",1,0))/nrow(baselineFracture)
# # of groups who fractured never        
# baselineFractureNever <- sum(ifelse(baselineFracture1$fracture=="0" & baselineFracture2$fracture=="0",1,0))/nrow(baselineFracture)
# conditionalProbBaseline <- matrix(c(baselineFracture12, baselineFractureOnly1, baselineFractureOnly2, baselineFractureNever),ncol=2,byrow=TRUE)
# colnames(conditionalProbBaseline) <- c("Ap frac","Ap no frac") 
# rownames(conditionalProbBaseline) <- c("A frac","A no frac")
# conditionalProbBaseline
```

```{r}
# kable(conditionalProbBaseline, "latex", caption = "Demo table", booktabs = T) %>%
# kable_styling(latex_options = c("striped", "hold_position"))
```

## 3B: Now investigating the big result: switch %: what's the % of pairs flipping their decisions?
# R consistencyprop
```{r, echo=TRUE}
## Convert format before merge: *this can be simplified*: 
treatmentFracture2$fracture <- as.numeric(treatmentFracture2$fracture) 
treatmentFracture1$fracture <- as.numeric(treatmentFracture1$fracture) 
treatmentFracture$consistent <- treatmentFracture2$fracture == treatmentFracture1$fracture

controlFracture1$fracture <- as.numeric(controlFracture1$fracture)
controlFracture2$fracture <- as.numeric(controlFracture2$fracture)
controlFracture$consistent <- controlFracture2$fracture == controlFracture1$fracture

treatmentConsistentSum <- sum(treatmentFracture$consistent) 
print(treatmentConsistentSum)
controlConsistentSum <- sum(controlFracture$consistent)
print(controlConsistentSum)

## Proportion test: 
prop.test(x = c(treatmentConsistentSum, controlConsistentSum), n = c(nrow(treatmentFracture), nrow(controlFracture)))

allFracture <- rbind(treatmentFracture, controlFracture)
consistencyTable <- table(allFracture$results.condition, allFracture$consistent)
allFracture$results.condition <- factor(x=allFracture$results.condition, levels=c("control", "treatment"))
chisq.test(consistencyTable)
```

# R consistencylogit
```{r, echo=TRUE}
## Logistic regression because Chi-square needs more observations in each cell
consistencyLogit <- glm(data=allFracture, consistent ~ results.condition, family="binomial")
summary(consistencyLogit)
stargazer(consistencyLogit, 
          covariate.labels = c("Masked (1: true)", "(Intercept)"),
          dep.var.labels=c("Consistent fracture"), 
          no.space=TRUE, 
          title="Consistency of fracture outcomes by condition. Masked teams decrease the log odds of a consistent outcome.", 
          label="tab:consistency", 
          #keep.stat="n",
          table.placement = "tb",
          star.cutoffs = c(0.05, 0.01, 0.001)
          )

## Chi goodness of fit: 
## Using baseline as theoretical probability distribution 
## Treatment: 
#chisq.test(treatmentAbsChange, p = baselineAbsChange/sum(baselineAbsChange)) 
#chisq.test(treatmentAbsChange, controlAbsChange, p=baselineAbsChange)
## Control:
#chisq.test(controlAbsChange,p=baselineAbsChange)
```

## Visualizing change: 
# R consistencygraph
```{r, echo=TRUE}
normalizedControlConsistency <- controlConsistentSum /nrow(controlFracture)
normalizedTreatmentConsistency <- treatmentConsistentSum / nrow(treatmentFracture)
normalizedControlConsistencySe <- sqrt(normalizedControlConsistency*(1-normalizedControlConsistency)/nrow(controlFracture))
normalizedTreatmentConsistencySe <- sqrt(normalizedTreatmentConsistency*(1-normalizedTreatmentConsistency)/nrow(treatmentFracture))

## Visualize differences: 
dat <- data.frame(FractureConsistency= factor(c("Masked","Unmasked"), levels=c("Masked","Unmasked")),
                  fractureValueSwitch = c(normalizedTreatmentConsistency, normalizedControlConsistency), SE=c(normalizedTreatmentConsistencySe, normalizedControlConsistencySe)) 

p <- ggplot(data=dat, aes(x=FractureConsistency, y=fractureValueSwitch)) +
  geom_bar(stat="identity", fill="#2853C2", alpha=0.7)+
  scale_y_continuous(labels = scales::percent_format(10)) + 
  geom_errorbar(aes(ymin=c(normalizedTreatmentConsistency-normalizedTreatmentConsistencySe,
                          normalizedControlConsistency-normalizedControlConsistencySe),
                    ymax=c(normalizedTreatmentConsistency+normalizedTreatmentConsistencySe,
                           normalizedControlConsistency+normalizedControlConsistencySe)), width = 0.1) +
  geom_text(aes(label=sprintf("%1.0f%%", round(fractureValueSwitch, 2)*100)), vjust=4.6, color="white")+ #size=8)+
  theme_classic() + labs(x="",
       y="Percent of repeated\n collaborations with consistent\n fracture outcomes") + theme_classic() 
  #theme(text = element_text(size=25),
  #      axis.text.x = element_text(size=16 )
  #      ) 
p
pdf('consistency.pdf', width=3.5, height=2.5)
p
dev.off();
```

## Visualizing meta-cognition differences: 
# R metaGraph
```{r}
individualProportionFracture$correctAnswers <- sum(individualProportionFracture$metaGuessedCorrectly) 

metaAnswersCorrect <- round(unique(individualProportionFracture$correctAnswers /nrow(individualProportionFracture)),2) 
metaAnswersSE <- round(unique(sqrt(metaAnswersCorrect*(1-metaAnswersCorrect)/nrow(individualProportionFracture))), 2)  

## Visualize differences: 
dat <- data.frame(fracturePrediction= factor(c("Correct fracture prediction"), levels=c("Correct fracture prediction")),
                  fracturePredictionCorrect = c(metaAnswersCorrect), SE=c(metaAnswersSE)) 

p <- ggplot(data=dat, aes(x=fracturePrediction, y=fracturePredictionCorrect)) +
  geom_bar(stat="identity", fill="#2853C2", alpha=0.7)+
  scale_y_continuous(labels = scales::percent_format(10)) + 
  geom_errorbar(aes(ymin=c(metaAnswersCorrect-metaAnswersSE),
                    ymax=c(metaAnswersCorrect+metaAnswersSE), width = 0.1)) +
  geom_text(aes(label=sprintf("%1.0f%%", round(fracturePredictionCorrect, 2)*100)), vjust=4.6, color="white")+ #size=8)+
  theme_classic() + labs(x="",
       y="Percent of individuals who accurately predicted \n \n partner's fracture score") + theme_classic() 
  #theme(text = element_text(size=25),
  #      axis.text.x = element_text(size=16 )
  #      ) 
p
pdf('metaPredictionQuestion.pdf', width=3.5, height=2.5)
p
dev.off();
```


## How much does individual predict fracture? 
# R baddudes
```{r}
library(lme4)
library(lmerTest)
library(pROC)



didpartnerfracture <- individualProportionFracture %>% 
  inner_join(individualProportionFracture, by = c("round", "batch", "room")) %>% 
  filter(id.x != id.y, condition.x != "Ap") %>%
  select(id.x, id.y, partnerFractured.x, results.condition.x, condition.x)
numrounds <- didpartnerfracture %>% 
  group_by(id.x) %>%
  summarise(count = n())
didpartnerfracture <- didpartnerfracture %>%
  inner_join(numrounds, by = c("id.x")) %>%
  filter(count > 1)

didpartnerfracture$partnerFractured.x.logical <- as.logical(didpartnerfracture$partnerFractured.x)
didpartnerfracture$id.x <- as.factor(didpartnerfracture$id.x)
didpartnerfracture$results.condition.x <- as.factor(didpartnerfracture$results.condition.x)
personlogit <- glmer(data = didpartnerfracture, partnerFractured.x ~ results.condition.x + (1|id.x), family="binomial")
summary(personlogit)
prob <- predict(personlogit, type=c("response"))
didpartnerfracture$prob <- prob

reduced <- glm(data = didpartnerfracture, partnerFractured.x ~ results.condition.x, family="binomial")
reducedprob <- predict(reduced, type=c("response"))
didpartnerfracture$reducedprob <- reducedprob

g <- roc(partnerFractured.x ~ prob, data=didpartnerfracture,plot=TRUE, auc.polygon=TRUE, max.auc.polygon=TRUE, grid=TRUE,  print.auc=TRUE, show.thres=TRUE)
g

g <- roc(partnerFractured.x ~ reducedprob, data=didpartnerfracture,plot=TRUE, auc.polygon=TRUE, max.auc.polygon=TRUE, grid=TRUE,  print.auc=TRUE, show.thres=TRUE)
g


```